---
name: "Kevin M. Middleton, Ph.D."
fontawesome: no
jobtitle: "Associate Professor"
department: "Department of Pathology and Anatomical Sciences"
university: "University of Missouri"
address: "1 Hospital Dr. • Columbia, MO 65212"
phone: 573-884-3192
email: "middletonk@missouri.edu"
github: kmiddleton
orcid: 0000-0003-4704-1064
scholar: Ziha7x8AAAAJ
web: middletonlab.org
date: "`r format(Sys.time(), '%B %Y')`"
titlecolor: "0726B2"
headcolor: "0726B2"
source: "github.com/kmiddleton/cv"
output: function(...) vitae::cv_document(..., template = "cvtemplate.tex", citation_package = "biblatex")
---

```{r setup, include=FALSE}

include_refs <- FALSE

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

library(tidyverse)
library(vitae)
library(RefManageR)
library(tinytex)
options(tinytex.verbose = TRUE)

# From https://github.com/robjhyndman/CV/blob/master/RobHyndmanCV.Rmd
baretable <- function(
  tbl, digits = 0,
  include.colnames = FALSE,
  include.rownames = FALSE,
  hline.after = NULL,
  size = getOption("xtable.size", NULL),
  add.to.row = getOption("xtable.add.to.row", NULL),
  ...) {
  tbl %>%
    xtable::xtable(digits = digits, ...) %>%
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      latex.environments = NULL,
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}

# https://github.com/ropenscilabs/vitae
# https://github.com/mitchelloharawild/CV/blob/master/CV.Rmd
# https://github.com/robjhyndman/CV/blob/master/RobHyndmanCV.Rmd
```

# Professional Experience

```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "Associate Professor", "University of Missouri", "Department of Pathology & Anatomical Sciences", "2012 - Pres.",
  "Associate Professor", "CSU San Bernardino", "Department of Biology", "2011 - 2012",
  "Assistant Professor", "CSU San Bernardino", "Department of Biology", "2007 - 2011",
  "NIH NRSA Postdoctoral Fellow", "Brown University and University of California, Riverside", "Effects of Genetics, Exercise, and Age on Bone Mechanics", "2005 - 2007",
  "Postdoctoral Research Associate", "Brown University", "Department of Ecology and Evolutionary Biology", "2003 - 2005"
) %>% 
  detailed_entries(degree, dates, uni, loc)
```

# Education

```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "BS Biology", "Wake Forest University", "Summa Cum Laude", "1992 - 1995",
  "PhD Ecology and Evolutionary Biology", "Brown University", "Morphology, evolution, and function of the avian hallux", "1996 - 2003"
) %>% 
  detailed_entries(degree, dates, uni, loc)
```

# Research Interests

My research focuses on musculoskeletal physiology, form, and function in the contexts of animal locomotion, feeding, and vertebrate evolution. In my work, I integrate studies across multiple scales from micro-scale structural materials of bone to macro-scale whole bone morphology to evolutionary changes across vertebrate taxa and with comparisons to extinct organisms.

## Current Projects

- Effects of exercise and genetic background on skeletal form, physiology, and biomechanics using high activity mice as a model organism
- Evolution of the avian head: integrating cranial biomechanics, muscle modeling, and brain evolution to understand avian cranial kinesis
- Development of Bayesian and machine learning models for the prediction of craniofacial growth and form in humans
- Evolution of wing-propelled diving in birds: exploring patterns of evolution in bone microstructure, feather biomechanics, functional morphology, and sensory systems

# Awards

```{r awards, results="asis"}
tribble(
  ~ Year, ~ Award,
  2017, "MU School of Medicine Awawrd for Outstanding Preclinical Faculty Education",
  2017, "Ann K. Covington Award for Undergraduate Mentoring",
  2019, "Gold Chalk Award for Graduate Teaching"
) %>%
  baretable()
```

# Grants in Review

\LTXtable{\textwidth}{grants_in_review.tex}

# Current and Past Grants and Fellowships

\LTXtable{\textwidth}{grants.tex}

# Publications

FIXME

- AAA 2019
- IADR talks
- Cleft palate talks
- SICB 2020 talks

- Alec paper
- Ian paper final

## Dissertation

```{r thesis}
if (include_refs) {
  bibliography_entries("Paperpile.bib") %>%
    filter(bibtype == "PhdThesis")
}
```

## Refereed Research Papers

```{r research-papers}
if (include_refs) {
bibliography_entries("Paperpile.bib") %>%
  filter(str_detect(keywords, "CV/Papers")) %>%
  arrange(year, author)
}
```

## Manuscripts in Review

```{r in-review}
if (include_refs) {
bibliography_entries("Paperpile.bib") %>%
  filter(str_detect(keywords, "CV/In review")) %>%
  arrange(year, author)
}
```

## Book Chapters

```{r book-chapters}
if (include_refs) {
bibliography_entries("Paperpile.bib") %>%
  filter(str_detect(keywords, "CV/Book chapters")) %>%
  arrange(year, author)
}
```

## Invited Reviews

```{r invited-reviews}
if (include_refs) {
bibliography_entries("Paperpile.bib") %>%
  filter(str_detect(keywords, "CV/Reviews")) %>%
  arrange(year, author)
}
```

## Book Reviews

```{r book-reviews}
if (include_refs) {
bibliography_entries("Paperpile.bib") %>%
  filter(str_detect(keywords, "CV/Book reviews")) %>%
  arrange(year, author)
}
```

## Published Data Sets

```{r datasets}
if (include_refs) {
bibliography_entries("Paperpile.bib") %>%
  filter(str_detect(keywords, "CV/Datasets")) %>%
  arrange(year, author)
}
```

## Manuscripts in Preparation

```{r in-prep}
if (include_refs) {
bibliography_entries("Paperpile.bib") %>%
  filter(str_detect(keywords, "CV/In prep")) %>%
  arrange(year, author)
}
```

## Published Abstracts

```{r abstracts}
if (include_refs) {
bibliography_entries("Paperpile.bib") %>%
  filter(str_detect(keywords, "CV/Abstracts")) %>%
  arrange(year, author)
}
```

## Other Presentations

```{r other}
if (include_refs) {
bibliography_entries("Paperpile.bib") %>%
  filter(str_detect(keywords, "CV/Other presentations")) %>%
  arrange(year, author)
}
```

# Teaching Experience

## University of Missouri

\LTXtable{\textwidth}{teaching.tex}

## California State University, San Bernardino

```{r results="asis"}
tribble(
  ~ Dates, ~ Course,
  "2007-2011", "Biology of the Chordates",
  "2008-2012", "Human Physiology and Anatomy",
  "2010-2012", "Biostatistics",
  "2008, 2010, 2012", "Graduate Seminar",
  "2008-2011", "Biology Seminar",
  "2008", "Advanced Vertebrate Morphology"
) %>% 
  baretable()
```

# Postdoctoral Supervisor

```{r results="asis"}
tribble(
  ~ Dates, ~ Name, ~ Notes,
  "2015-2018", "Alida Bailleul, PhD", "Currently a postdoctoral research associate at the Institute of Vertebrate Paleontology and Paleoanthropology, Beijing"
) %>% 
  detailed_entries(when = Dates, what = Name, where = Notes)
```

# Graduate Advisor

```{r results="asis"}
tribble(
  ~ Dates, ~ Name, ~ Degree, ~ Notes,
  "2015-2019", "Sarah Peacock", "Ph.D. University of Missouri", "Currently Outreach Coordinator at the Boston Museum of Science",
  "2013-2018", "Amanda Smolinsky", "Ph.D. University of Missouri", "Currently a Postdoctoral Research Associate at Rocky Vista University",
  "2011-2012", "Katherine Johnson", "M.S., CSUSB", "Completed doctoral studies at University of California, Riverside",
  "2010-2012", "Brittney Coats", "M.S., CSUSB", "Completed doctoral studies at the University of Chicago",
  "2008-2012", "Susan Lujan", "M.S., CSUSB", "Currently a lecturer at California State University, San Bernardino"
) %>% 
  detailed_entries(when = Dates, what = Name, with = Degree, where = Notes)
```

# Graduate Committee Member

## Current

```{r results="asis"}
tribble(
  ~ Dates, ~ Name, ~ Notes,
  "2019-Present", "Mikaela Pulsipher", "M.S.; Geological Sciences",
  "2018-Present", "Sean Greer", "Ph.D.; Pathobiology",
  "2017-Present", "Faye McGechie", "Ph.D.; Pathobiology",
  "2017-Present", "Rebecca Dirkes", "Ph.D.; Nutrition & Exercise Physiology",
  "2016-Present", "Kaleb Sellers", "Ph.D.; Pathobiology",
  "2016-Present", "Melanie Boeyer", "Ph.D.; Pathobiology",
  "2016-Present", "Samuel Sullivan", "Ph.D.; Pathobiology",
  "2016-Present", "Elizabeth Cho", "Ph.D.; Anthropology",
  "2016-Present", "Deise Cruz", "Ph.D.; Biological Sciences",
  "2015-Present", "Rob'yn Johnston", "Ph.D.; Anthropology",
  "2015-Present", "Sharon Kuo", "Ph.D.; Pathobiology"
) %>% 
  detailed_entries(when = Dates, what = Name, with = Notes)
```

## Past

```{r results="asis"}
tribble(
  ~ Dates, ~ Name, ~ Degree, ~ Notes,
  "2018-2019", "Ellee Cook", "Ph.D.; Biological Sciences",
  "2015-2019", "Ian Cost", "Ph.D.; Pathobiology",
  "2017-2018", "Landry Konan", "M.S.; Pathology and Anatomical Sciences", "",
  "2017-2018", "Stephanie Rosbach", "M.S.; Geological Sciences", "",
  "2016-2018", "Tara Selly", "Ph.D.; Geological Sciences", "",
  "2015-2017", "Edward Ramirez", "Ph.D.; Biological Sciences", "",
  "2015-2017", "Steven Hanson", "Ph.D.; Pathobiology", "",
  "2014-2017", "Luésoni Johnson", "Ph.D.; Biological Sciences", "",
  "2013-2016", "Elizabeth Moffett", "Ph.D.; Biological Sciences", "Currently an Assistant Professor at Rocky Vista University",
  "2014-2015", "Kaleb Sellers", "M.S.; Pathology", "",
  "2012-2015", "Henry Tsai", "Ph.D.; Pathobiology", "Currently an Assistant Professor at Missouri State University",
  "2009-2012", "Kandee Bain", "M.S.; Biology, CSUSB", "",
  "2008-2012", "Kim Scott", "M.S.; Biology, CSUSB", "",
  "2007-2008", "Adam Huttenlocker", "M.S.; Biology, CSUSB", "Currently an Assistant Professor at the University of Southern California",
  "2007-2008", "Candace Reno", "M.S.; Biology, CSUSB", ""
) %>% 
  detailed_entries(when = Dates, what = Name, with = Degree, where = Notes)
```

# Undergraduate Mentoring

University of Missouri only. 23 additional students} at Brown University and UC Riverside; 2003--2012

```{r results="asis"}
tribble(
  ~ Dates, ~ Name, ~ Notes,
  "2019-Present", "Joshua Fajardo", "",
  "2018", "Kendra Lewis", "MU School of Medicine Summer Research Intern from Washington University in St. Louis",
  "2016-Present", "Alec Wilken", "",
  "2016-2018", "Caitlyn Smith", "",
  "2016-2018", "Rebecca Meyer", "",
  "2016-2017", "Nicholas Ferrari", "",
  "2016", "Jake Cooper", "NSF Inside Dinosaurs Research Fellow",
  "2016", "Eva Herbst", "NSF Inside Dinosaurs Research Fellow",
  "2014-2018", "Nicholas Bira", "C3 Hughes Research Fellow",
  "2015", "Kyle Kirkland", "MU School of Medicine Summer Research Intern from Michigan State University",
  "2014-2015", "Imran Rashid", "",
  "2014-2015", "Michael Sojka", "C3 Hughes Research Fellow, MU School of Journalism",
  "2014", "Tarrin Casey", "MU School of Medicine Summer Research Intern from Xavier University, New Orleans",
  "2013", "Diana Salas", "MU School of Medicine Summer Research Intern from Indiana University"
) %>% 
  detailed_entries(when = Dates, what = Name, where = Notes)
```

# Invited Seminars

```{r results="asis"}
tribble(
  ~ Date, ~ Location,
  "2001", "University of Chicago",
  "2001", "American Museum of Natural History",
	"2007", "CSU, San Bernardino",
  "2007", "University of California, Riverside",
  "2007", "CSU, Fullerton",
  "2007", "Loma Linda University",
  "2010", "Grove High School, Redlands, CA",
  "2010", "CSU, Northridge",
  "2011", "University of Missouri",
  "2012", "La Sierra College",
  "2012", "Grinnell College",
  "2013", "MU Evolutionary Studies EvoBlitz",
  "2013", "University of Texas at Austin",
  "2013", "Saint Louis University",
  "2013", "MU Division of Biological Sciences",
  "2014", "Northeast Ohio Medical University",
  "2014", "MU Math in Life Sciences Freshman Interest Group",
  "2014", "MU LSUROP Evening Seminar Speaker"
) %>% 
  baretable()
```

# Professional Service

## Referee

- Acta Anatomica
- Acta Palaeontologica Polonica
- Acta Zoologica Sinica
- Ameghiniana
- American Journal of Physical Anthropology
- Anatomical Record
- Biology Letters
- Comparative Biochemistry and Physiology
- Current Biology
- Evolution
- IEEE Visualization & Graphics
- International Journal of Primatology
- Journal of Anatomy
- Journal of Morphology
- Journal of Vertebrate Paleontology
- Journal of Zoology
- Nature
- Nature Communications
- Naturwissenschaften
- Palaeontology
- Paleobiology
- Paleobios
- PeerJ
- PLoS One
- Proceedings of the National Academy of Sciences USA
- Proceedings of the Royal Society (Biological Sciences)
- Quarterly Review of Biology
- Restoration Ecology
- Royal Society Open Science
- Zoological Journal of the Linnean Society
- Zoology

## NSF Panel Service

```{r results="asis"}
tribble(
  ~ Date, ~ Service,
  "2012", "Division of Evolutionary Biology -- Systematics and Biodiversity Science"
) %>% 
  baretable()
```

## NSF Ad Hoc Reviewer

```{r results="asis"}
tribble(
  ~ Date, ~ Service,
  "2009", "National Science Foundation -- IOB",
  "2010", "National Science Foundation -- DEB",
  "2012", "National Science Foundation -- IOB",
  "2017", "National Science Foundation -- IOB"
) %>% 
  baretable()
```

## University of Missouri Research Board

```{r results="asis"}
tribble(
  ~ Date, ~ Service,
  "2015", "Ad hoc reviewer"
) %>% 
  baretable()
```

## Reviewer (Textbooks)

```{r results="asis"}
tribble(
  ~ Date, ~ Service, ~ Publisher,
  "2003", "Miller, KR and JS Levine. Biology", "Pearson-Prentice Hall",
  "2010", "Tate, P. Anatomy and Physiology", "McGraw Hill",
  "2010", "Biological Sciences Curriculum Studies. BSCS Biology: A Human Approach. 4th Ed.", "Kendall Hunt Publishing"
) %>% 
  baretable()
```

## Reviewer for Deutsche Forschungsgemeinschaft (German Research Foundation)

```{r results="asis"}
tribble(
  ~ Date, ~ Service,
  "2018", "Life Sciences 1: Molecular and Organismic Biology"
) %>% 
  baretable()
```

# Department and University Service

## Current

```{r results="asis"}
tribble(
  ~ Date, ~ Service,
  "2018-Present", "MU School of Medicine Faculty Committee for Diversity and Inclusion",
  "2016-Present", "Evolution and Social Science Group (ESS) steering committee",
  "2015-Present", "School of Medicine Advice Support and Career (ASC) Preclerkship Advisor",
  "2014-Present", "School of Medicine Block 2 Planning Committee",
  "2014-Present", "School of Medicine eResources Committee",
  "2013-Present", "PAS Director of Admissions",
  "2013-Present", "PAS Promotion and Tenure Committee",
  "2012-Present", "MU Doctoral Faculty",
  "2012-Present", "MU Graduate Faculty",
  "2012-Present", "Pathobiology Area Program Faculty"
) %>% 
  baretable()
```

## Past

```{r results="asis"}
tribble(
  ~ Date, ~ Service,
  "2016-2019", "MU School of Medicine Admissions Committee",
  "2016-2019", "MU Information Technology Committee",
  "2016-2018", "MU Library Committee",
  "2016", "Chair, MU Life Sciences Week Genetics, Evolution, and Environment Poster Competition",
  "2016", "MU Office of Undergraduate Research focus group",
  "2015", "Life Sciences Undergraduate Research Opportunity Program Selection Committee",
  "2014-2018", "MU Life Sciences Week poster competition judge",
  "2013-2017", "PAS Director of Graduate Studies",
  "2013-2016, 2019", "SOM Summer Research Internship in Medical Sciences Selection Committee",
  "2013, 2015-2019", "PAS Assistant Teaching Professor Search Committee",
  "2013-2019", "PAS Lecturer Search Committee",
  "2013-2014", "School of Medicine Block 4 Planning Committee"
) %>% 
  baretable()
```

*California State University, San Bernardino*

```{r results="asis"}
tribble(
  ~ Date, ~ Service,
	"2009-2012", "Institutional Animal Care and Use Committee",
	"2008-2012", "NSF Mathematics and Science Scholars Mentor",
	"2007-2012", "Pre-Dental Club Faculty Advisor",
	"2007-2012", "Health Professions Advisory Committee",
	"2007-2012", "Biology Department Webmaster",
	"2009", "College of Natural Sciences Outstanding Students Evaluation Committee"
) %>% 
  baretable()
```

# Professional Organizations

- American Association of Anatomists
- International Society of Vertebrate Morphology
- Society of Avian Paleontology and Evolution
- Society of Integrative and Comparative Biology
- Society of Vertebrate Paleontology

# Televised Outreach

\LTXtable{\textwidth}{televised.tex}
