%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Kevin Middleton, Ph.D.}{}

\position{Associate Professor}
\address{Department of Pathology and Anatomical Sciences, University of
Missouri School of Medicine}

\email{\href{mailto:middletonk@missouri.edu}{\nolinkurl{middletonk@missouri.edu}}}
\homepage{middletonlab.org}
\orcid{0000-0003-4704-1064}
\github{kmiddleton}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{ltxtable}
\usepackage{multicol}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {January 2021}
    {Kevin Middleton, Ph.D.~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{professional-experience}{%
\section{Professional Experience}\label{professional-experience}}

\begin{cventries}
    \cventry{Associate Professor}{University of Missouri}{Department of Pathology \& Anatomical Sciences}{2012 - Pres.}{}\vspace{-4.0mm}
    \cventry{Associate Professor}{CSU San Bernardino}{Department of Biology}{2011 - 2012}{}\vspace{-4.0mm}
    \cventry{Assistant Professor}{CSU San Bernardino}{Department of Biology}{2007 - 2011}{}\vspace{-4.0mm}
    \cventry{NIH NRSA Postdoctoral Fellow}{Brown University and University of California, Riverside}{Effects of Genetics, Exercise, and Age on Bone Mechanics}{2005 - 2007}{}\vspace{-4.0mm}
    \cventry{Postdoctoral Research Associate}{Brown University}{Department of Ecology and Evolutionary Biology}{2003 - 2005}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{BS Biology}{Wake Forest University}{Summa Cum Laude}{1992 - 1995}{}\vspace{-4.0mm}
    \cventry{PhD Ecology and Evolutionary Biology}{Brown University}{Morphology, evolution, and function of the avian hallux}{1996 - 2003}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{research-interests}{%
\section{Research Interests}\label{research-interests}}

My research focuses on musculoskeletal physiology, form, and function in
the contexts of animal locomotion, feeding, and vertebrate evolution. In
my work, I integrate studies across multiple scales from micro-scale
structural materials of bone to macro-scale whole bone morphology to
evolutionary changes across vertebrate taxa and with comparisons to
extinct organisms.

\hypertarget{current-projects}{%
\subsection{Current Projects}\label{current-projects}}

\begin{itemize}
\tightlist
\item
  Effects of exercise and genetic background on skeletal form,
  physiology, and biomechanics using high activity mice as a model
  organism
\item
  Evolution of the avian head: integrating cranial biomechanics, muscle
  modeling, and brain evolution to understand avian cranial kinesis
\item
  Development of Bayesian and machine learning models for the prediction
  of craniofacial growth and form in humans
\item
  Evolution of wing-propelled diving in birds: exploring patterns of
  evolution in bone microstructure, feather biomechanics, functional
  morphology, and sensory systems
\end{itemize}

\hypertarget{awards}{%
\section{Awards}\label{awards}}

\begin{tabular}{rl}
  2017 & MU School of Medicine Award for Outstanding Preclinical Faculty Education \\ 
  2017 & Ann K. Covington Award for Undergraduate Mentoring \\ 
  2019 & Gold Chalk Award for Graduate Teaching \\ 
  \end{tabular}

\hypertarget{grants-in-review}{%
\section{Grants in Review}\label{grants-in-review}}

\LTXtable{\textwidth}{grants_in_review.tex}

\hypertarget{current-and-past-grants-and-fellowships}{%
\section{Current and Past Grants and
Fellowships}\label{current-and-past-grants-and-fellowships}}

\LTXtable{\textwidth}{grants.tex}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{dissertation}{%
\subsection{Dissertation}\label{dissertation}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_dissertation}{}
\leavevmode\hypertarget{ref-middleton_morphology_2003}{}%
Middleton, K. M. (2003). \emph{Morphology evolution and function of the
avian hallux} {[}PhD thesis{]}. Brown University.

\endgroup

\hypertarget{refereed-research-papers}{%
\subsection{Refereed Research Papers}\label{refereed-research-papers}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_papers}{}
\leavevmode\hypertarget{ref-Boeyer2020-jn}{}%
Boeyer, M. E., Middleton, K. M., Duren, D. L., \& Leary, E. V. (2020).
Estimating peak height velocity in individuals: A comparison of
statistical methods. \emph{Ann. Hum. Biol.}, \emph{47}(5), 434--445.
\url{https://doi.org/10.1080/03014460.2020.1763458}

\leavevmode\hypertarget{ref-Boeyer2020-hp}{}%
Boeyer, M. E., Middleton, K. M., Duren, D. L., \& Leary, E. V. (2020).
Estimating peak height velocity in individuals: A response to Cole
(2020). \emph{Annals of Human Biology}.
\url{https://doi.org/10.1080/03014460.2020.1837954}

\leavevmode\hypertarget{ref-Cost2020-jo}{}%
Cost, I. N., Middleton, K. M., Sellers, K. C., Echols, M. S., Witmer, L.
M., Davis, J. L., \& Holliday, C. M. (2020). Palatal biomechanics and
its significance for cranial kinesis in \emph{Tyrannosaurus rex}.
\emph{Anat. Rec.}, \emph{303}(4), 999--1017.
\url{https://doi.org/10.1002/ar.24219}

\leavevmode\hypertarget{ref-Sherwood2020-le}{}%
Sherwood, R. J., Oh, H., Valiathan, M., McNulty, K., Duren, D. L.,
Knigge, R., Hardin, A., Holzhauser, C. L., \& Middleton, K. M. (2020).
Bayesian approach to longitudinal craniofacial growth: The craniofacial
growth consortium study. \emph{Anat. Rec.}
\url{https://doi.org/10.1002/ar.24520}

\leavevmode\hypertarget{ref-Tsai2020-zm}{}%
Tsai, H. P., Middleton, K. M., Hutchinson, J. R., \& Holliday, C. M.
(2020). More than one way to be a giant: Convergence and disparity in
the hip joints of saurischian dinosaurs. \emph{Evolution}, \emph{74}(8),
1654--1681. \url{https://doi.org/10.1111/evo.14017}

\leavevmode\hypertarget{ref-Wilken2020-wf}{}%
Wilken, A. T., Sellers, K. C., Cost, I. N., Rozin, R. E., Middleton, K.
M., \& Holliday, C. M. (2020). Connecting the chondrocranium:
Biomechanics of the suspensorium in reptiles. \emph{Vertebrate Zoology},
\emph{70}(3), 275--290. \url{https://doi.org/10.26049/VZ70-3-2020-02}

\leavevmode\hypertarget{ref-Lynch2019-ny}{}%
Lynch, R., Lummaa, V., Panchanathan, K., Middleton, K., Rotkirch, A.,
Danielsbacka, M., O'Brien, D., \& Loehr, J. (2019). Integration involves
a trade-off between fertility and status for World War II evacuees.
\emph{Nat Hum Behav}, \emph{3}(4), 337--345.
\url{https://doi.org/10.1038/s41562-019-0542-5}

\leavevmode\hypertarget{ref-Ngoma2019-gq}{}%
Ng'oma, E., Fidelis, W., Middleton, K. M., \& King, E. G. (2019). The
evolutionary potential of diet-dependent effects on lifespan and
fecundity in a multi-parental population of \emph{Drosophila
melanogaster}. \emph{Heredity}, \emph{122}(5), 582--594.
\url{https://doi.org/10.1038/s41437-018-0154-2}

\leavevmode\hypertarget{ref-Sullivan2019-vq}{}%
Sullivan, S. P., McGechie, F. R., Middleton, K. M., \& Holliday, C. M.
(2019). 3D muscle architecture of the pectoral muscles of european
starling (\emph{Sturnus vulgaris}). \emph{Integr Org Biol}, \emph{1}(1),
oby010. \url{https://doi.org/10.1093/iob/oby010}

\leavevmode\hypertarget{ref-Wilken2019-so}{}%
Wilken, A. T., Middleton, K. M., Sellers, K. C., Cost, I. N., \&
Holliday, C. M. (2019). The roles of joint tissues and jaw muscles in
palatal biomechanics of the savannah monitor (\emph{Varanus
exanthematicus}) and their significance for cranial kinesis. \emph{J.
Exp. Biol.}, \emph{222}(Pt 18), 1--14.
\url{https://doi.org/10.1242/jeb.201459}

\leavevmode\hypertarget{ref-Ngoma2018-aw}{}%
Ng'oma, E., King, E. G., \& Middleton, K. M. (2018). A model-based high
throughput method for fecundity estimation in fruit fly studies.
\emph{Fly}, \emph{12}(3-4), 183--190.
\url{https://doi.org/10.1080/19336934.2018.1562267}

\leavevmode\hypertarget{ref-Peacock2018-ty}{}%
Peacock, S. J., Coats, B. R., Kirkland, J. K., Tanner, C. A., Garland,
T., Jr, \& Middleton, K. M. (2018). Predicting the bending properties of
long bones: Insights from an experimental mouse model. \emph{Am. J.
Phys. Anthropol.}, \emph{165}(3), 457--470.
\url{https://doi.org/10.1002/ajpa.23363}

\leavevmode\hypertarget{ref-Peacock2018-uz}{}%
Peacock, S. J., Garland, T., Jr, \& Middleton, K. M. (2018). Reply to
Ruff, Warden, and Karlson. \emph{Am. J. Phys. Anthropol.},
\emph{167}(1), 190--193. \url{https://doi.org/10.1002/ajpa.23614}

\leavevmode\hypertarget{ref-Tsai2018-xp}{}%
Tsai, H. P., Middleton, K. M., Hutchinson, J. R., \& Holliday, C. M.
(2018). Hip joint articular soft tissues of non-dinosaurian
Dinosauromorpha and early dinosauria: Evolutionary and biomechanical
implications for Saurischia. \emph{J. Vert. Paleontol.},
\emph{e1427593}, 1--23.
\url{https://doi.org/10.1080/02724634.2017.1427593}

\leavevmode\hypertarget{ref-Goller2017-es}{}%
Goller, B., Segre, P. S., Middleton, K. M., Dickinson, M. H., \&
Altshuler, D. L. (2017). Visual sensory signals dominate tactile cues
during docked feeding in hummingbirds. \emph{Front. Neurosci.},
\emph{11}, 622. \url{https://doi.org/10.3389/fnins.2017.00622}

\leavevmode\hypertarget{ref-Sellers2017-kj}{}%
Sellers, K. C., Middleton, K. M., Davis, J. L., \& Holliday, C. M.
(2017). Ontogeny of bite force in a validated biomechanical model of the
american alligator. \emph{J. Exp. Biol.}, \emph{220}, 2036--2046.
\url{https://doi.org/10.1242/jeb.156281}

\leavevmode\hypertarget{ref-Malisch2016-ht}{}%
Malisch, J. L., deWolski, K., Meek, T. H., Acosta, W., Middleton, K. M.,
Crino, O. L., \& Garland, T., Jr. (2016). Acute restraint stress alters
wheel-running behavior immediately following stress and up to 20 hours
later in house mice. \emph{Physiol. Biochem. Zool.}, \emph{89}(6),
546--552. \url{https://doi.org/10.1086/688660}

\leavevmode\hypertarget{ref-read_hummingbirds_2016}{}%
Read, T. J. G., Segre, P. S., Middleton, K. M., \& Altshuler, D. L.
(2016). Hummingbirds control turning velocity using body orientation and
turning radius using asymmetrical wingbeat kinematics. \emph{J. R. Soc.
Interface}, \emph{13}(116), 20160110.
\url{https://doi.org/10.1098/rsif.2016.0110}

\leavevmode\hypertarget{ref-cheney_membrane_2014}{}%
Cheney, J. A., Konow, N., Middleton, K. M., Breuer, K. S., Roberts, T.
J., Giblin, E. L., \& Swartz, S. M. (2014). Membrane muscle function in
the compliant wings of bats. \emph{Bioinspir. Biomim.}, \emph{9}(2),
025007. \url{https://doi.org/10.1088/1748-3182/9/2/025007}

\leavevmode\hypertarget{ref-altshuler_wingbeat_2012}{}%
Altshuler, D. L., Quicazán-Rubio, E. M., Segre, P. S., \& Middleton, K.
M. (2012). Wingbeat kinematics and motor control of yaw turns in anna's
hummingbirds (\emph{Calypte anna}). \emph{J. Exp. Biol.}, \emph{215}(Pt
23), 4070--4084. \url{https://doi.org/10.1242/jeb.075044}

\leavevmode\hypertarget{ref-keeney_sex_2012}{}%
Keeney, B. K., Meek, T. H., Middleton, K. M., Holness, L. F., \&
Garland, T., Jr. (2012). Sex differences in cannabinoid receptor-1 (CB1)
pharmacology in mice selectively bred for high voluntary wheel-running
behavior. \emph{Pharmacol. Biochem. Behav.}, \emph{101}(4), 528--537.
\url{https://doi.org/10.1016/j.pbb.2012.02.017}

\leavevmode\hypertarget{ref-garlandjr_how_2011}{}%
Garland, T., Jr, Kelly, S. A., Malisch, J. L., Kolb, E. M., Hannon, R.
M., Keeney, B. K., Van Cleave, S. L., \& Middleton, K. M. (2011). How to
run far: Multiple solutions and sex-specific responses to selective
breeding for high voluntary activity levels. \emph{Proc. Biol. Sci.},
\emph{278}(1705), 574--581. \url{https://doi.org/10.1098/rspb.2010.1584}

\leavevmode\hypertarget{ref-kolb_erythropoietin_2010}{}%
Kolb, E. M., Kelly, S. A., Middleton, K. M., Sermsakdi, L. S., Chappell,
M. A., \& Garland, T., Jr. (2010). Erythropoietin elevates VO2,max but
not voluntary wheel running in mice. \emph{J. Exp. Biol.},
\emph{213}(3), 510--519. \url{https://doi.org/10.1242/jeb.029074}

\leavevmode\hypertarget{ref-middleton_variation_2010}{}%
Middleton, K. M., Goldstein, B. D., Guduru, P. R., Waters, J. F., Kelly,
S. A., Swartz, S. M., \& Garland, T., Jr. (2010). Variation in
within-bone stiffness measured by nanoindentation in mice bred for high
levels of voluntary wheel running. \emph{J. Anat.}, \emph{216}(1),
121--131. \url{https://doi.org/10.1111/j.1469-7580.2009.01175.x}

\leavevmode\hypertarget{ref-riskin_effect_2010}{}%
Riskin, D. K., Iriarte-Díaz, J., Middleton, K. M., Breuer, K. S., \&
Swartz, S. M. (2010). The effect of body size on the wing movements of
pteropodid bats, with insights into thrust and lift production. \emph{J.
Exp. Biol.}, \emph{213}(Pt 23), 4110--4122.
\url{https://doi.org/10.1242/jeb.043091}

\leavevmode\hypertarget{ref-wallace_functional_2010}{}%
Wallace, I. J., Middleton, K. M., Lublinsky, S., Kelly, S. A., Judex,
S., Garland, T., Jr, \& Demes, B. (2010). Functional significance of
genetic variation underlying limb bone diaphyseal structure. \emph{Am.
J. Phys. Anthropol.}, \emph{143}(1), 21--30.
\url{https://doi.org/10.1002/ajpa.21286}

\leavevmode\hypertarget{ref-eisenmann_day_2009}{}%
Eisenmann, J. C., Wickel, E. E., Kelly, S. A., Middleton, K. M., \&
Garland, T., Jr. (2009). Day-to-day variability in voluntary wheel
running among genetically differentiated lines of mice that vary in
activity level. \emph{Eur. J. Appl. Physiol.}, \emph{106}(4), 613--619.
\url{https://doi.org/10.1007/s00421-009-1056-z}

\leavevmode\hypertarget{ref-malisch_behavioral_2009}{}%
Malisch, J. L., Breuner, C. W., Kolb, E. M., Wada, H., Hannon, R. M.,
Chappell, M. A., Middleton, K. M., \& Garland, T., Jr. (2009).
Behavioral despair and home-cage activity in mice with chronically
elevated baseline corticosterone concentrations. \emph{Behav. Genet.},
\emph{39}(2), 192--201. \url{https://doi.org/10.1007/s10519-008-9246-8}

\leavevmode\hypertarget{ref-clarke_mosaicism_2008}{}%
Clarke, J. A., \& Middleton, K. M. (2008). Mosaicism, modules, and the
evolution of birds: Results from a bayesian approach to the study of
morphological evolution using discrete character data. \emph{Syst.
Biol.}, \emph{57}(2), 185--201.
\url{https://doi.org/10.1080/10635150802022231}

\leavevmode\hypertarget{ref-hannon_phenotypic_2008a}{}%
Hannon, R. M., Kelly, S. A., Middleton, K. M., Kolb, E. M., Pomp, D., \&
Garland, T., Jr. (2008). Phenotypic effects of the ``mini-muscle''
allele in a large HR x C57BL/6J mouse backcross. \emph{J. Hered.},
\emph{99}(4), 349--354. \url{https://doi.org/10.1093/jhered/esn011}

\leavevmode\hypertarget{ref-keeney_differential_2008}{}%
Keeney, B. K., Raichlen, D. A., Meek, T. H., Wijeratne, R. S.,
Middleton, K. M., Gerdeman, G. L., \& Garland, T., Jr. (2008).
Differential response to a selective cannabinoid receptor antagonist
(SR141716: Rimonabant) in female mice from lines selectively bred for
high voluntary wheel-running behaviour. \emph{Behav. Pharmacol.},
\emph{19}(8), 812--820.
\url{https://doi.org/10.1097/FBP.0b013e32831c3b6b}

\leavevmode\hypertarget{ref-lavin_morphometrics_2008}{}%
Lavin, S. R., Karasov, W. H., Ives, A. R., Middleton, K. M., \& Garland,
T., Jr. (2008). Morphometrics of the avian small intestine compared with
that of nonflying mammals: A phylogenetic approach. \emph{Physiol.
Biochem. Zool.}, \emph{81}(5), 526--550.
\url{https://doi.org/10.1086/522641}

\leavevmode\hypertarget{ref-middleton_selective_2008a}{}%
Middleton, K. M., Kelly, S. A., \& Garland, T., Jr. (2008). Selective
breeding as a tool to probe skeletal response to high voluntary
locomotor activity in mice. \emph{Integr. Comp. Biol.}, \emph{48}(3),
394--410. \url{https://doi.org/10.1093/icb/icn057}

\leavevmode\hypertarget{ref-middleton_relative_2008}{}%
Middleton, K. M., Shubin, C. E., Moore, D. C., Carter, P. A., Garland,
T., Jr, \& Swartz, S. M. (2008). The relative importance of genetics and
phenotypic plasticity in dictating bone morphology and mechanics in aged
mice: Evidence from an artificial selection experiment. \emph{Zoology},
\emph{111}(2), 135--147.
\url{https://doi.org/10.1016/j.zool.2007.06.003}

\leavevmode\hypertarget{ref-swartz_biomechanics_2008}{}%
Swartz, S. M., \& Middleton, K. M. (2008). Biomechanics of the bat limb
skeleton: Scaling, material properties and mechanics. \emph{Cells
Tissues Organs}, \emph{187}(1), 59--84.
\url{https://doi.org/10.1159/000109964}

\leavevmode\hypertarget{ref-tian_direct_2006}{}%
Tian, X., Iriarte-Diaz, J., Middleton, K., Galvao, R., Israeli, E.,
Roemer, A., Sullivan, A., Song, A., Swartz, S., \& Breuer, K. (2006).
Direct measurements of the kinematics and dynamics of bat flight.
\emph{Bioinspir. Biomim.}, \emph{1}(4), S10--8.
\url{https://doi.org/10.1088/1748-3182/1/4/S02}

\leavevmode\hypertarget{ref-middleton_morphological_2001}{}%
Middleton, K. M. (2001). The morphological basis of hallucal orientation
in extant birds. \emph{J. Morphol.}, \emph{250}(1), 51--60.
\url{https://doi.org/10.1002/jmor.1058}

\leavevmode\hypertarget{ref-middleton_theropod_2000}{}%
Middleton, K. M., \& Gatesy, S. M. (2000). Theropod forelimb design and
evolution. \emph{Zool. J. Linn. Soc.}, \emph{128}(2), 149--187.
\url{https://doi.org/10.1111/j.1096-3642.2000.tb00160.x}

\leavevmode\hypertarget{ref-gatesy_theropod_1999}{}%
Gatesy, S. M., \& Middleton, K. M. (1999). Theropod hind limb disparity
revisited: A response. \emph{J. Vert. Paleontol.}, \emph{19}(3),
606--606. \url{https://doi.org/10.1080/02724634.1999.10011173}

\leavevmode\hypertarget{ref-gatesy_three-dimensional_1999}{}%
Gatesy, S. M., Middleton, K. M., Jenkins, F. A., Jr, \& Shubin, N. H.
(1999). Three-dimensional preservation of foot movements in Triassic
theropod dinosaurs. \emph{Nature}, \emph{399}(6732), 141--144.
\url{https://doi.org/10.1038/20167}

\leavevmode\hypertarget{ref-gatesy_bipedalism_1997}{}%
Gatesy, S. M., \& Middleton, K. M. (1997). Bipedalism, flight, and the
evolution of theropod locomotor diversity. \emph{J. Vert. Paleontol.},
\emph{17}(2), 308--329.
\url{https://doi.org/10.1080/02724634.1997.10010977}

\endgroup

\hypertarget{book-chapters}{%
\subsection{Book Chapters}\label{book-chapters}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_bookchapters}{}
\leavevmode\hypertarget{ref-owerkowicz_respiratory_2015}{}%
Owerkowicz, T., Musinsky, C., Middleton, K. M., \& Crompton, A. W.
(2015). Respiratory turbinates and the evolution of endothermy in
mammals and birds. In K. P. Dial, N. H. Shubin, \& E. L. Brainerd
(Eds.), \emph{Great transformations in vertebrate evolution} (pp.
143--166). University of Chicago Press.
\url{https://doi.org/10.7208/chicago/9780226268392.003.0009}

\leavevmode\hypertarget{ref-gatesy_skeletal_2007}{}%
Gatesy, S. M., \& Middleton, K. M. (2007). Skeletal adaptations for
flight. In B. K. Hall (Ed.), \emph{Fins into limbs}. University of
Chicago Press.

\endgroup

\hypertarget{invited-reviews}{%
\subsection{Invited Reviews}\label{invited-reviews}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_reviews}{}
\leavevmode\hypertarget{ref-middleton_challenges_2015}{}%
Middleton, K. M., \& English, L. T. (2014). Challenges and advances in
the study of pterosaur flight. \emph{Can. J. Zool.}, \emph{93}(12),
945--959. \url{https://doi.org/10.1139/cjz-2013-0219}

\leavevmode\hypertarget{ref-clarke_bird_2006}{}%
Clarke, J., \& Middleton, K. (2006). Bird evolution. \emph{Curr. Biol.},
\emph{16}(10), R350--4. \url{https://doi.org/10.1016/j.cub.2006.04.023}

\endgroup

\hypertarget{book-reviews}{%
\subsection{Book Reviews}\label{book-reviews}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_bookreviews}{}
\leavevmode\hypertarget{ref-middleton_dinosaurs_2003}{}%
Middleton, K. M. (2003). \emph{Dinosaurs of the air: The evolution and
loss of flight in dinosaurs and birds} and \emph{mesozoic birds: Above
the heads of dinosaurs}. \emph{Palaeontol. Electronica}, \emph{6}, 5.
\url{http://palaeo-electronica.org/2003_1/books/birds.htm}

\endgroup

\hypertarget{published-data-sets}{%
\subsection{Published Data Sets}\label{published-data-sets}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_datasets}{}
\leavevmode\hypertarget{ref-Ngoma2018-kf}{}%
Ng'oma, E., Fidelis, W., Middleton, K. M., \& King, E. G. (2018).
\emph{Lifespan and fecundity data for: The evolutionary potential of
diet-dependent effects on lifespan and fecundity in a multi-parental
population of \textup{drosophila melanogaster}}.
\url{https://zenodo.org/record/1285237}

\leavevmode\hypertarget{ref-Peacock2018-lc}{}%
Peacock, S. J., Coats, B. R., Kirkland, J. K., Tanner, C. A., Garland,
T., Jr, \& Middleton, K. M. (2018). \emph{Data from: Predicting the
bending properties of long bones: Insights from an experimental mouse
model}. \url{https://osf.io/3wxnh/}

\leavevmode\hypertarget{ref-read_data_2016}{}%
Read, T. J. G., Segre, P. S., Middleton, K. M., \& Altshuler, D. L.
(2016). \emph{Data from: Hummingbirds control turning velocity using
body orientation and turning radius using asymmetrical wingbeat
kinematics}.
\url{https://datadryad.org/stash/dataset/doi:10.5061/dryad.j77h6}

\leavevmode\hypertarget{ref-middleton_data_2000}{}%
Middleton, K. M., \& Gatesy, S. M. (2000). \emph{Data from: Theropod
forelimb design and evolution}.
\url{https://doi.org/10.5061/dryad.jf6ht}

\endgroup

\hypertarget{manuscripts-in-preparation}{%
\subsection{Manuscripts in
Preparation}\label{manuscripts-in-preparation}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_inprep}{}
\leavevmode\hypertarget{ref-Cost_undated-cr}{}%
Cost, I. N., Sellers, K. C., Middleton, K. M., \& Holliday, C. M.
(n.d.-). Conveying 3D spatial data of muscle orientation throughout
lineages, their ontogeny, and their feeding cycles to understand cranial
mechanics. \emph{Proc. Natl. Acad. Sci. U. S. A.}

\leavevmode\hypertarget{ref-kuo_tensile_inreview}{}%
Kuo, S., \& Middleton, K. M. (n.d.-). Tensile mechanical properties of
isolated penguin flipper feathers. \emph{J. Morphol.}

\leavevmode\hypertarget{ref-Lujan_undated-rq}{}%
Lujan, S. L., Owerkowicz, T., Hicks, J. W., \& Middleton, K. M. (n.d.-).
Atmospheric oxygen level does not alter growth or size-specific femoral
cross-sectional geometry in the american alligator (\emph{alligator
mississippiensis}). \emph{Anat. Rec.}

\leavevmode\hypertarget{ref-Middleton_undated-dc}{}%
Middleton, K. M., Prior, S. C., \& Swartz, S. M. (n.d.-). Scaling of
cortical and subchondral bone thickness in the femora of terrestrial
mammals. \emph{J. Morphol.}

\leavevmode\hypertarget{ref-Smith_undated-hm}{}%
Smith, C. J., Holliday, C. M., Middleton, K. M., \& Bailleul, A. M.
(n.d.-). Bending properties of the jugal bone in mallard ducks and its
significance for cranial biomechanics. \emph{Anatomical Record}.

\leavevmode\hypertarget{ref-Smolinsky_undated-uh}{}%
Smolinsky, A. N., \& Middleton, K. M. (n.d.-). Endurance and impact
activities differentially influence femoral cross-sectional geometry and
mineral apposition. \emph{J. Exp. Biol.}

\leavevmode\hypertarget{ref-smolinsky_mechanical_inpreparation}{}%
Smolinsky, A. N., Middleton, K. M., \& Holliday, C. M. (n.d.-).
Mechanical properties of the mandibular symphysis of american alligators
(\emph{alligator mississippiensis}). \emph{J. Exp. Biol.}

\endgroup

\hypertarget{postdoctoral-supervisor}{%
\section{Postdoctoral Supervisor}\label{postdoctoral-supervisor}}

\begin{cventries}
    \cventry{Currently an Assistant Professor at the Institute of Vertebrate Paleontology and Paleoanthropology, Beijing}{Alida Bailleul, PhD}{}{2015-2018}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{graduate-advisor}{%
\section{Graduate Advisor}\label{graduate-advisor}}

\begin{cventries}
    \cventry{Currently Assistant Teaching Professor at Northeastern University}{Sarah Peacock}{Ph.D. University of Missouri}{2015-2019}{}\vspace{-4.0mm}
    \cventry{Currently an Assistant Teaching Professor at Roanoke College}{Amanda Smolinsky}{Ph.D. University of Missouri}{2013-2018}{}\vspace{-4.0mm}
    \cventry{Completed doctoral studies at University of California, Riverside}{Katherine Johnson}{M.S., CSUSB}{2011-2012}{}\vspace{-4.0mm}
    \cventry{Completed doctoral studies at the University of Chicago}{Brittney Coats}{M.S., CSUSB}{2010-2012}{}\vspace{-4.0mm}
    \cventry{Currently a lecturer at California State University, San Bernardino}{Susan Lujan}{M.S., CSUSB}{2008-2012}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{graduate-committee-member}{%
\section{Graduate Committee Member}\label{graduate-committee-member}}

\hypertarget{current}{%
\subsection{Current}\label{current}}

\begin{cventries}
    \cventry{Ph.D.; Geological Sciences}{Gabriel Jacobs}{}{2020-Present}{}\vspace{-4.0mm}
    \cventry{Ph.D.; Biological Sciences}{Christian Perez}{}{2020-Present}{}\vspace{-4.0mm}
    \cventry{Ph.D.; Pathobiology}{Emily Lessner}{}{2019-Present}{}\vspace{-4.0mm}
    \cventry{Ph.D.; Pathobiology}{Samuel Sullivan}{}{2019-Present}{}\vspace{-4.0mm}
    \cventry{M.S.; Geological Sciences}{Mikaela Pulsipher}{}{2019-Present}{}\vspace{-4.0mm}
    \cventry{Ph.D.; Pathobiology}{Sean Greer}{}{2018-Present}{}\vspace{-4.0mm}
    \cventry{Ph.D.; Pathobiology}{Kaleb Sellers}{}{2016-Present}{}\vspace{-4.0mm}
    \cventry{Ph.D.; Anthropology}{Elizabeth Cho}{}{2016-Present}{}\vspace{-4.0mm}
    \cventry{Ph.D.; Biological Sciences}{Deise Cruz}{}{2016-Present}{}\vspace{-4.0mm}
    \cventry{Ph.D.; Anthropology}{Rob'yn Johnston}{}{2015-Present}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{past}{%
\subsection{Past}\label{past}}

\begin{cventries}
    \cventry{Currently podtdoctoral researcher, University of Chicago}{Faye McGechie}{Ph.D.; Pathobiology}{2017-2020}{}\vspace{-4.0mm}
    \cventry{Currently pursuing certificate in nutrition, University of Missouri}{Rebecca Dirkes}{Ph.D.; Nutrition \& Exercise Physiology}{2017-2020}{}\vspace{-4.0mm}
    \cventry{Currently doctoral student at University of Chicago}{Alec Wilken}{M.S.; Pathology and Anatomical Sciences}{2019-2020}{}\vspace{-4.0mm}
    \cventry{Currently postdoctoral research associate at the University of Missouri}{Melanie Boeyer}{Ph.D.; Pathobiology}{2016-2020}{}\vspace{-4.0mm}
    \cventry{Currently postdoctoral research associate at Pennsylvania State University}{Sharon Kuo}{Ph.D.; Pathobiology}{2015-2020}{}\vspace{-4.0mm}
    \cventry{}{Ellee Cook}{Ph.D.; Biological Sciences}{2018-2019}{}\vspace{-4.0mm}
    \cventry{Currently assistant professor at Albright College}{Ian Cost}{Ph.D.; Pathobiology}{2015-2019}{}\vspace{-4.0mm}
    \cventry{}{Landry Konan}{M.S.; Pathology and Anatomical Sciences}{2017-2018}{}\vspace{-4.0mm}
    \cventry{}{Stephanie Rosbach}{M.S.; Geological Sciences}{2017-2018}{}\vspace{-4.0mm}
    \cventry{Currently research associate at the University of Missouri}{Tara Selly}{Ph.D.; Geological Sciences}{2016-2018}{}\vspace{-4.0mm}
    \cventry{}{Edward Ramirez}{Ph.D.; Biological Sciences}{2015-2017}{}\vspace{-4.0mm}
    \cventry{}{Steven Hanson}{Ph.D.; Pathobiology}{2015-2017}{}\vspace{-4.0mm}
    \cventry{}{Luésoni Johnson}{Ph.D.; Biological Sciences}{2014-2017}{}\vspace{-4.0mm}
    \cventry{Currently an Assistant Professor at Rocky Vista University}{Elizabeth Moffett}{Ph.D.; Biological Sciences}{2013-2016}{}\vspace{-4.0mm}
    \cventry{}{Kaleb Sellers}{M.S.; Pathology}{2014-2015}{}\vspace{-4.0mm}
    \cventry{Currently an Assistant Professor at Missouri State University}{Henry Tsai}{Ph.D.; Pathobiology}{2012-2015}{}\vspace{-4.0mm}
    \cventry{}{Kandee Bain}{M.S.; Biology, CSUSB}{2009-2012}{}\vspace{-4.0mm}
    \cventry{}{Kim Scott}{M.S.; Biology, CSUSB}{2008-2012}{}\vspace{-4.0mm}
    \cventry{Currently an Assistant Professor at the University of Southern California}{Adam Huttenlocker}{M.S.; Biology, CSUSB}{2007-2008}{}\vspace{-4.0mm}
    \cventry{}{Candace Reno}{M.S.; Biology, CSUSB}{2007-2008}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{undergraduate-mentoring}{%
\section{Undergraduate Mentoring}\label{undergraduate-mentoring}}

University of Missouri only. 23 additional students at Brown University
and UC Riverside; 2003--2012

\begin{cventries}
    \cventry{MU Cherng Summer Scholar}{Madison LaChance}{}{2020-Present}{}\vspace{-4.0mm}
    \cventry{}{Joshua Fajardo}{}{2019-Present}{}\vspace{-4.0mm}
    \cventry{MU School of Medicine Summer Research Intern from Washington University in St. Louis}{Kendra Lewis}{}{2018}{}\vspace{-4.0mm}
    \cventry{Currently Master's student at the University of Missouri}{Alec Wilken}{}{2016-2019}{}\vspace{-4.0mm}
    \cventry{Currently a student in the University of Missouri School of Medicine}{Caitlyn Smith}{}{2016-2018}{}\vspace{-4.0mm}
    \cventry{}{Rebecca Meyer}{}{2016-2018}{}\vspace{-4.0mm}
    \cventry{}{Nicholas Ferrari}{}{2016-2017}{}\vspace{-4.0mm}
    \cventry{NSF Inside Dinosaurs Research Fellow}{Jake Cooper}{}{2016}{}\vspace{-4.0mm}
    \cventry{NSF Inside Dinosaurs Research Fellow}{Eva Herbst}{}{2016}{}\vspace{-4.0mm}
    \cventry{C3 Hughes Research Fellow}{Nicholas Bira}{}{2014-2018}{}\vspace{-4.0mm}
    \cventry{MU School of Medicine Summer Research Intern from Michigan State University}{Kyle Kirkland}{}{2015}{}\vspace{-4.0mm}
    \cventry{}{Imran Rashid}{}{2014-2015}{}\vspace{-4.0mm}
    \cventry{C3 Hughes Research Fellow, MU School of Journalism}{Michael Sojka}{}{2014-2015}{}\vspace{-4.0mm}
    \cventry{Currently a student in the University of Missouri School of Medicine}{Tarrin Casey}{}{2014}{}\vspace{-4.0mm}
    \cventry{MU School of Medicine Summer Research Intern from Indiana University}{Diana Salas}{}{2013}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

\hypertarget{published-abstracts}{%
\subsection{Published Abstracts}\label{published-abstracts}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_abstracts}{}
\leavevmode\hypertarget{ref-Middleton2020-ye}{}%
Middleton, K. M., Hardin, A. M., Knigge, R. P., Duren, D. L., Mcnulty,
K. P., Valiathan, M., \& Sherwood, R. J. (2020). \emph{Bayesian
modelling to address the challenges of estimating craniofacial growth
patterns}. International Association for Dental Research.

\leavevmode\hypertarget{ref-Fortner2020-qa}{}%
Fortner, J. D., Wilkin, A. T., Cost, I. N., Sellers, K. C., Middleton,
K. M., \& Holliday, C. M. (2020). \emph{The role of symphyseal tissues
and sutures on mandible function in archosaurs}. Society of Vertebrate
Palentology Annual Meeting.

\leavevmode\hypertarget{ref-Holliday2020-ua}{}%
Holliday, C. M., \& Middleton, K. M. (2020). \emph{Myology of the
reptilia}. Experimental Biology.

\leavevmode\hypertarget{ref-Holliday2020-vt}{}%
Holliday, C. M., Wilken, A. T., Sullivan, S., Lessner, E., Sellers, K.
C., Middleton, K. M., \& Ward, C. V. (2020). \emph{Paleontology
engagement in rural public science expos}. Society of Vertebrate
Paleontology Annual Meeting.

\leavevmode\hypertarget{ref-Holliday2020-to}{}%
Holliday, C. M., Wilkin, A. T., Sullivan, S., Verhulst, C., Sellers, K.
C., Lessner, E., Fortner, J. D., \& Middleton, K. M. (2020).
\emph{Myology of the reptilia: 3d modeling of jaw muscles and its
utility in paleobiology}. Society of Vertebrate Palentology Annual
Meeting.

\leavevmode\hypertarget{ref-Lough2020-qg}{}%
Lough, C. P., Gieg, S. D., Bezold, W. A., Feltz, K. P., Middleton, K.
M., \& Skelley, N. W. (2020). \emph{Mechanical properties of 3D printed
orthopaedic internal fixation implants}. ORS 2020 Annual Meeting.

\leavevmode\hypertarget{ref-Sellers2020-gf}{}%
Sellers, K. C., Middleton, K. M., \& Holliday, C. M. (2020). \emph{Joint
loading and transformation in suchian evolution}. Society for
Experimental Biology.

\leavevmode\hypertarget{ref-Sellers2020-lz}{}%
Sellers, K. C., Middleton, K. M., \& Holliday, C. M. (2020).
\emph{Muscle and joint evolution in crocodyliforms}. Experimental
Biology.

\leavevmode\hypertarget{ref-Sullivan2020-jk}{}%
Sullivan, S. P., Middleton, K. M., \& Holliday, C. M. (2020).
\emph{Evolutionary variation and biomechanics of the avian furcula}.
Experimental Biology.

\leavevmode\hypertarget{ref-Sullivan2020-df}{}%
Sullivan, S. P., Middleton, K. M., \& Holliday, C. M. (2020).
\emph{Morphology and function of the avian furcula}. Society for
Experimental Biology.

\leavevmode\hypertarget{ref-Wilken2020-ws}{}%
Wilken, A. T., Middleton, K. M., Sellers, K. C., Cost, I. N., \&
Holliday, C. M. (2020). \emph{Functional morphology of the palate of
varanus exanthematicus and its significance for the evolution of cranial
kinesis}. Society for Experimental Biology.

\leavevmode\hypertarget{ref-Wilken2020-ks}{}%
Wilken, A. T., Sellers, K. C., Rozin, R., Middleton, K. M., \& Holliday,
C. M. (2020). \emph{Comparative biomechanics of the otic joint and
suspensorium in sauropsids}. Society of Vertebrate Paleontology Annual
Meeting.

\leavevmode\hypertarget{ref-Holliday2019-tp}{}%
Holliday, C. M., Wilken, A. T., Bailleul, A. M., Sellers, K. C., Cost,
I. N., Rozin, R. E., \& Middleton, K. M. (2019). \emph{Connecting the
chondrocranium: Biomechanics of the palatocranial joints of sauropsids}.
International Congress of Vertebrate Morphology.

\leavevmode\hypertarget{ref-McGechie2019-xy}{}%
McGechie, F., Sullivan, S., Middleton, K. M., Holliday, C. M., Nalley,
T. K., Grider-Potter, N., \& Ward, C. V. (2019). 3D analysis of primate
neck anatomy using Contrast-Enhanced CT imaging, Fascicle-Tracking
algorithms, and muscle mechanics. \emph{FASEB J.}, \emph{612.1}.

\leavevmode\hypertarget{ref-McGechie2019-ov}{}%
McGechie, F., Sullivan, S., Middleton, K. M., Holliday, C. M., Nalley,
T. K., Grider-Potter, N., \& Ward, C. V. (2019). Using novel 3D
techniques to visualize and quantify primate neck anatomy. \emph{Am. J.
Phys. Anthropol.}, \emph{168}(S68), 160.

\leavevmode\hypertarget{ref-Middleton2019-ll}{}%
Middleton, K. M., Sellers, K. C., Cost, I. N., Spates, A. T., \&
Holliday, C. M. (2019). \emph{Methods for visualizing and comparing
force vectors in two- and Three-Dimensions, with applications for
vertebrate feeding and locomotion}. International Congress of Vertebrate
Morphology.

\leavevmode\hypertarget{ref-Middleton2019-si}{}%
Middleton, K. M., Smolinsky, A. N., \& Garland, T., Jr. (2019). Creation
of a novel inbred mouse model for high activity with a small muscle
phenotype. \emph{FASEB J.}, \emph{769.1}.

\leavevmode\hypertarget{ref-Owerkowicz2019-hc}{}%
Owerkowicz, T., Poff, M., Middleton, K. M., \& Crompton, A. W. (2019).
\emph{Metabolic and environmental factors shaping the morphology of
respiratory turbinates in mammals and archosaurs}. International
Congress of Vertebrate Morphology.

\leavevmode\hypertarget{ref-Ruth2019-mq}{}%
Ruth, A. A., \& Middleton, K. M. (2019). Mechanical stimulus vs.
Selection in determining enthesis morphology in mice. \emph{Am. J. Phys.
Anthropol.}, \emph{168}(S68), 212.

\leavevmode\hypertarget{ref-Sellers2019-js}{}%
Sellers, K. C., Middleton, K. M., \& Holliday, C. M. (2019). \emph{Joint
loading and transformation in suchian evolution}. International Congress
of Vertebrate Morphology.

\leavevmode\hypertarget{ref-Smolinsky2019-lf}{}%
Smolinsky, A. N., Aldridge, K., Castro, A. A., Garland, T., Jr, \&
Middleton, K. M. (2019). Artificial selection for increased voluntary
wheel running alters limb skeleton shape and exercise plasticity in
mice. \emph{FASEB J.}, \emph{10.6}.

\leavevmode\hypertarget{ref-Smolinsky2019-in}{}%
Smolinsky, A. N., Aldridge, K., Castro, A. A., Garland, T., Jr, \&
Middleton, K. M. (2019). \emph{Effects of artificial selection for
increased voluntary wheel running on hindlimb skeletal shape in mice}.
International Congress of Vertebrate Morphology.

\leavevmode\hypertarget{ref-Sullivan2019-yv}{}%
Sullivan, S. P., Middleton, K. M., \& Holliday, C. M. (2019).
\emph{Morphology and function of the avian furcula}. International
Congress of Vertebrate Morphology.

\leavevmode\hypertarget{ref-Wilken2019-up}{}%
Wilken, A. T., Middleton, K. M., Sellers, K. C., Cost, I. N., \&
Holliday, C. M. (2019). \emph{Functional morphology of the palate in
\textup{varanus exanthematicus} (squamata: Varanidae) and its
significance for the evolution of cranial kinesis}. International
Congress of Vertebrate Morphology.

\leavevmode\hypertarget{ref-Cost2018-lx}{}%
Cost, I. N., Middleton, K. M., \& Holliday, C. M. (2018).
\emph{Mechanical performance in the skulls of parrots (aves:
Psittaciformes)}. Society for Integrative and Comparative Biology.

\leavevmode\hypertarget{ref-Holliday2018-nh}{}%
Holliday, C. M., Cost, I. N., Sellers, K. C., \& Middleton, K. M.
(2018). \emph{Using ternary plots to convey 3D jaw muscle orientation in
space and time}. Society for Integrative and Comparative Biology.

\leavevmode\hypertarget{ref-McGechie2018-sd}{}%
McGechie, F., Aldridge, K., \& Middleton, K. M. (2018). Plastic and
evolved responses to postural behavior in the morphology of the cranium.
\emph{Am. J. Phys. Anthropol.}, \emph{165}, 171.

\leavevmode\hypertarget{ref-Owerkowicz2018-hr}{}%
Owerkowicz, T., Middleton, K. M., \& Crompton, A. W. (2018). Selective
forces behind the evolution of respiratory turbinates in mammals and
birds. \emph{5th International Palaeontological Congress}, 893.

\leavevmode\hypertarget{ref-Sellers2018-lh}{}%
Sellers, K. C., Middleton, K. M., Clark, J. M., \& Holliday, C. M.
(2018). \emph{Cranial joints and the evolution of extreme feeding
performance in crocodyliformes}. Society of Vertebrate Palentology
Annual Meeting.

\leavevmode\hypertarget{ref-Sellers2018-sc}{}%
Sellers, K. C., Middleton, K. M., \& Holliday, C. M. (2018).
\emph{Biomechanics and evolution of the crocodyliform skull}. Society
for Integrative and Comparative Biology.

\leavevmode\hypertarget{ref-Sethi2018-ga}{}%
Sethi, A., Sellers, K. C., Cost, I. N., McGechie, F., Middleton, K. M.,
\& Holliday, C. M. (2018). \emph{3D fiber tracking of jaw muscles
reveals a diversity of muscle architectures in the heads of reptiles}.
Society for Integrative and Comparative Biology.

\leavevmode\hypertarget{ref-Smith2018-kz}{}%
Smith, C. J., Middleton, K. M., Bailleul, A. M., \& Holliday, C. M.
(2018). \emph{Bending properties of the lower temporal bar in ducks and
its significance for cranial biomechanics}. Society for Integrative and
Comparative Biology.

\leavevmode\hypertarget{ref-Smolinsky2018-iz}{}%
Smolinsky, A. N., Aldridge, K., \& Middleton, K. M. (2018).
Muscle-intensive and high-impact exercises differentially influence
whole bone 3D morphology in young male mice. \emph{FASEB J.}, \emph{32},
9650.

\leavevmode\hypertarget{ref-Smolinsky2018-sy}{}%
Smolinsky, A. N., \& Middleton, K. M. (2018). \emph{Muscle- and
impact-dominated activities differentially affect bone morphology and
mineral apposition in young outbred mice}. Society for Integrative and
Comparative Biology.

\leavevmode\hypertarget{ref-Sullivan2018-kt}{}%
Sullivan, S. P., Holliday, C. M., Bailleul, A. M., \& Middleton, K. M.
(2018). \emph{Digital reconstruction of the avian pectoral girdle with
implications for furcula function}. Society for Integrative and
Comparative Biology.

\leavevmode\hypertarget{ref-Wilkin2018-ya}{}%
Wilkin, A. T., Middleton, K. M., Sellers, K. C., Cost, I. N., \&
Holliday, C. M. (2018). \emph{Finite element analysis of the savannah
monitor, \textup{varanus exanthematicus}, and its implications for
lepidosaur cranial kinesis}. Society for Integrative and Comparative
Biology.

\leavevmode\hypertarget{ref-cost_biomechanics_2017}{}%
Cost, I. N., Middleton, K. M., Witmer, L. M., Echols, M. S., \&
Holliday, C. M. (2017). Biomechanics of the feeding apparatus of parrots
(aves: Psittaciformes). \emph{FASEB J.}, \emph{31}(Supplement 1), 577.7.

\leavevmode\hypertarget{ref-hill_aaa_2017}{}%
Hill, C. A., Aldridge, K., Holliday, C. M., Middleton, K. M., Ward, C.
V., Maiolino, S., \& Jorgensen, M. E. (2017). The minute clinic:
Increasing student engagement in an undergraduate Systems-Based anatomy
course. \emph{FASEB J.}, \emph{31}(Supplement 1), 733.8.

\leavevmode\hypertarget{ref-holliday_dinosaurs_2017}{}%
Holliday, C. M., Hill, C. A., Davis, J. L., Witmer, L. M., \& Middleton,
K. M. (2017). Inside Dinosaurs: A broader impacts program for research,
teaching and public education through dinosaur biology, physics and
evolution. \emph{FASEB J.}, \emph{31}(Supplement 1), 734.8.

\leavevmode\hypertarget{ref-peacock_effects_2017}{}%
Peacock, S. J., Bates, K. A., Talton, O. O., Schulz, L. C., \&
Middleton, K. M. (2017). Effects of perinatal circadian programming on
activity and skeletal morphology in C57BL/6 mice. \emph{FASEB J.},
\emph{31}(Supplement 1), 577.18.

\leavevmode\hypertarget{ref-Sellers2017-uj}{}%
Sellers, K. C., Middleton, K. M., Davis, J. L., \& Holliday, C. M.
(2017). Biomechanics and the evolution of the crocodyliform skull.
\emph{FASEB J.}, \emph{31}(Supplement 1), 579.1.

\leavevmode\hypertarget{ref-Smith2017-ws}{}%
Smith, C. J., Holliday, C. M., Middleton, K. M., \& Bailleul, A. M.
(2017). Bending properties of the jugal bone in mallard ducks and its
significance for cranial biomechanics. \emph{FASEB J.},
\emph{31}(Supplement 1), 577.6.

\leavevmode\hypertarget{ref-smolinsky_comparing_2017}{}%
Smolinsky, A. N., \& Middleton, K. M. (2017). Comparing femur
cross-sectional morphology in young outbred mice following daily
exposure to muscle-, impact-, or combined loading of the hind limb
skeleton. \emph{FASEB J.}, \emph{31}(Supplement 1), 577.15.

\leavevmode\hypertarget{ref-Smolinsky2017-gk}{}%
Smolinsky, A. N., \& Middleton, K. M. (2017). The effects of muscle- and
impact-dominated loading on femoral cross-section morphology and mineral
apposition in young outbred mice. \emph{Integr. Comp. Biol.},
\emph{57}(Suppl. 1), e395.

\leavevmode\hypertarget{ref-tsai_cartilage_2017}{}%
Tsai, H. P., Middleton, K. M., \& Holliday, C. M. (2017). \emph{The
cartilage cone of archosauromorphs: Implications for hip loading and
femoral ossification}. Society for Integrative and Comparative Biology
Annual Meeting.

\leavevmode\hypertarget{ref-wilkin_modeling_2017}{}%
Wilkin, A. T., Middleton, K. M., Sellers, K. C., Cost, I. N., Davis, J.
L., \& Holliday, C. M. (2017). Modeling complex cranial joints in
\emph{varanus exanthematicus}. \emph{FASEB J.}, \emph{31}(Supplement 1),
577.5.

\leavevmode\hypertarget{ref-cost_postural_2016}{}%
Cost, I. N., Sellers, K. C., Davis, J. L., Middleton, K. M., Witmer, L.
M., \& Holliday, C. M. (2016). Postural changes and kinetic competency
in the palates of birds and other diapsids. \emph{Journal of Vertebrate
Paleontology, Program and Abstracts}, \emph{2016}(Supplement 1),
120--121.

\leavevmode\hypertarget{ref-cost_relative_2016}{}%
Cost, I. N., Spates, A., Sellers, K. C., Davis, J. L., Middleton, K. M.,
Witmer, L. M., \& Holliday, C. M. (2016). Relative kinetic competency in
the palatal complexes of birds and other diapsids. \emph{Anat. Rec.},
\emph{299}(special feature), 208--209.

\leavevmode\hypertarget{ref-holliday_dinosaurs_2016}{}%
Holliday, C. M., Hill, C. A., Davis, J. L., Witmer, L. M., \& Middleton,
K. M. (2016). Inside dinosaurs: A broader impacts program for research,
teaching and public education through dinosaur biology, physics and
evolution. \emph{Journal of Vertebrate Paleontology, Program and
Abstracts}, \emph{2016}, 155--156.

\leavevmode\hypertarget{ref-kuo_tensile_2016}{}%
Kuo, S., \& Middleton, K. M. (2016). \emph{Tensile mechanical properties
of isolated penguin flipper feathers}. Society for Integrative and
Comparative Biology 2016 Annual Meeting. Portland, OR.

\leavevmode\hypertarget{ref-lujan_atmospheric_2016}{}%
Lujan, S. L., Owerkowicz, T., Elsey, R. M., Hicks, J. W., \& Middleton,
K. M. (2016). Atmospheric oxygen conditions do not constrain growth or
biomechanical performance of limb bones in alligatoridae:
\emph{Alligator mississippiensis}. \emph{Anat. Rec.}, \emph{299}(special
feature), 72--73.

\leavevmode\hypertarget{ref-middleton_scaling_2016}{}%
Middleton, K. M., Hurtado, A. C., \& Swartz, S. M. (2016). Scaling of
haversian systems in a phylogenetically diverse sample of mammals is
consistent with physical and physiological constraints. \emph{Anat.
Rec.}, \emph{299}(special feature), 70.

\leavevmode\hypertarget{ref-middleton_comparison_2016}{}%
Middleton, K. M., Peacock, S. J., Kirkland, J. K., \& Garland, T., Jr.
(2016). Comparison of morphology and bending mechanics of femora in
response to chronic exercise in three strains of mice. \emph{FASEB J.},
\emph{30}, 368.2.

\leavevmode\hypertarget{ref-peacock_history_2016}{}%
Peacock, S. J., Coats, B. R., Kirkland, J. K., Tanner, C. A., Garland,
T., Jr., \& Middleton, K. M. (2016). \emph{History of exercise,
cross-sectional geometry, and bending mechanics: Inferences based on
three strains of mice}. American Association of Physical
Anthropologists. Atlanta, GA.

\leavevmode\hypertarget{ref-sellers_high_2016}{}%
Sellers, K. C., Davis, J. L., Middleton, K. M., \& Holliday, C. M.
(2016). A high-fidelity, 3D model of the skull of Alligator
mississippiensis (Archosauria: Crocodylia) and its significance for
vertebrate feeding biomechanics. \emph{Anat. Rec.}, \emph{299}(special
feature), 120--121.

\leavevmode\hypertarget{ref-sellers_biomechanics_2016}{}%
Sellers, K. C., Davis, J. L., Middleton, K. M., \& Holliday, C. M.
(2016). Biomechanics and the evolution of the crocodyliform skull.
\emph{Journal of Vertebrate Paleontology, Program and Abstracts},
\emph{2016}, 221.

\leavevmode\hypertarget{ref-smolinsky_comparison_2016}{}%
Smolinsky, A. N., \& Middleton, K. M. (2016). Comparison of impact
loading and wheel running on femoral cross-section morphology in young
outbred mice. \emph{Anat. Rec.}, \emph{299}(special feature), 246.

\leavevmode\hypertarget{ref-spates_using_2016}{}%
Spates, A., Cost, I. N., Sellers, K. C., Middleton, K. M., \& Holliday,
C. M. (2016). Using novel methods to visualize jaw muscle biomechanics
and its significance for the evolution of the avian feeding apparatus.
\emph{FASEB J.}, \emph{30}, 779.6.

\leavevmode\hypertarget{ref-tsai_cartilage_2016a}{}%
Tsai, H. P., Middleton, K. M., \& Holliday, C. M. (2016). The cartilage
cone of archosauromorphs: Biomechanical implications for hip joint
loading and femoral ossification. \emph{Anat. Rec.}, \emph{299}(special
feature), 197.

\leavevmode\hypertarget{ref-tsai_cartilage_2016}{}%
Tsai, H. P., Middleton, K. M., \& Holliday, C. M. (2016). The cartilage
cone of archosauromorphs: Implications of chondro-osseous junction on
hip joint loading and femoral ossification. \emph{Journal of Vertebrate
Paleontology, Program and Abstracts}, \emph{2016}, 239.

\leavevmode\hypertarget{ref-cheney_shaping_2015}{}%
Cheney, J. A., Konow, N., Middleton, K. M., Breuer, K. S., Roberts, T.
J., Giblin, E. L., \& Swartz, S. M. (2015). Shaping the wings of bats:
Muscle and wing skin interactions in flight. \emph{Integr. Comp. Biol.},
\emph{55}, e29.

\leavevmode\hypertarget{ref-cost_biomechanics_2015}{}%
Cost, I. N., Spates, A., Sellers, K. C., Davis, J. L., Middleton, K. M.,
Witmer, L. M., \& Holliday, C. M. (2015). Biomechanics of the avian
feeding apparatus. \emph{Journal of Vertebrate Paleontology, Program and
Abstracts}, \emph{2015}, 110.

\leavevmode\hypertarget{ref-sellers_ontogeny_2015}{}%
Sellers, K. C., Davis, J. L., Middleton, K. M., \& Holliday, C. M.
(2015). Ontogeny and biomechanics of the american alligator skull.
\emph{Journal of Vertebrate Paleontology, Program and Abstracts},
\emph{2015}, 211.

\leavevmode\hypertarget{ref-smolinsky_material_2015}{}%
Smolinsky, A. N., Middleton, K. M., Pfeiffer, F., \& Holliday, C. M.
(2015). Material properties of the mandibular symphysis in
\emph{alligator mississippiensis}. \emph{Integr. Comp. Biol.},
\emph{55}, e173.

\leavevmode\hypertarget{ref-tsai_solutions_2015}{}%
Tsai, H. P., Middleton, K. M., \& Holliday, C. M. (2015). Solutions for
gigantism: Evolutionary and biomechanical implications of dinosaur hip
joint soft tissues. \emph{FASEB J.}, \emph{29}(supplement), 351.4.

\leavevmode\hypertarget{ref-harper-judd_dinosaurs_2014}{}%
Harper-Judd, J., Holliday, C. M., Knocke, M., Butaric, L. N., George, I.
D., Middleton, K. M., Moffett, E. A., Swartz, S., Tsai, H. P., \&
Warren, A. L. (2014). Dinosaurs \& cavemen science expo: Science
outreach using interactive and experiential anatomical learning.
\emph{Journal of Vertebrate Paleontology, Program and Abstracts},
\emph{2014}, 241.

\leavevmode\hypertarget{ref-holliday_modeling_2014}{}%
Holliday, C. M., Sellers, K. C., Davis, J. L., Middleton, K. M., \&
Witmer, L. M. (2014). Modeling cranial biomechanics in archosaurs using
3D computational methods. \emph{Journal of Vertebrate Paleontology,
Program and Abstracts}, \emph{2014}, 149.

\leavevmode\hypertarget{ref-lujan_acute_2014}{}%
Lujan, S. L., Owerkowicz, T., Elsey, R. M., Hicks, J. W., \& Middleton,
K. M. (2014). Acute and chronic alterations in atmospheric oxygen do not
alter femoral biomechanics in \emph{alligator mississippiensis}.
\emph{Integr. Comp. Biol.}, \emph{54}, e308.

\leavevmode\hypertarget{ref-middleton_analysis_2014}{}%
Middleton, K. M., \& Altshuler, D. L. (2014). \emph{Analysis of motor
variability in the maneuvering flight of hummingbirds}. World Congress
of Biomechanics. Boston, MA.

\leavevmode\hypertarget{ref-middleton_estimating_2014}{}%
Middleton, K. M., Johnson, K. E., \& Clarke, J. A. (2014). Estimating
bending mechanics of extant and fossil penguin contour feathers.
\emph{Ornithol. Sci.}, \emph{13}(supplement), 144.

\leavevmode\hypertarget{ref-proffitt_patterns_2014a}{}%
Proffitt, J. V., Middleton, K. M., \& Clarke, J. A. (2014). Patterns of
morphological evolution during a locomotor transition: Lessons from the
evolution of wing-propelled diving in penguins. \emph{Integr. Comp.
Biol.}, \emph{54}, e334.

\leavevmode\hypertarget{ref-proffitt_patterns_2014}{}%
Proffitt, J. V., Middleton, K. M., \& Clarke, J. A. (2014). Patterns of
morphological evolution during the evolution of wing-propelled diving in
penguins: Insights into the evolution of form and function.
\emph{Ornithol. Sci.}, \emph{13}(supplement), 342.

\leavevmode\hypertarget{ref-tsai_archosaur_2014}{}%
Tsai, H. P., Middleton, K. M., \& Holliday, C. M. (2014). Archosaur hip
joint and its significance in body size and locomotor evolution.
\emph{Integr. Comp. Biol.}, \emph{54}, e211.

\leavevmode\hypertarget{ref-tsai_more_2014a}{}%
Tsai, H. P., Middleton, K. M., \& Holliday, C. M. (2014). More than one
way to be a giant: Convergence and disparity in saurischian dinosaur hip
joints during body size evolution. \emph{Integr. Comp. Biol.},
\emph{55}, e186.

\leavevmode\hypertarget{ref-cheney_electromyography_2013}{}%
Cheney, J. A., Middleton, K. M., Konow, N., Giblin, E. L., Breuer, K.
S., \& Swartz, S. M. (2013). Electromyography of bat wing membrane
muscles. \emph{Integr. Comp. Biol.}, \emph{53}, e34.

\leavevmode\hypertarget{ref-johnson_comparative_2013}{}%
Johnson, K. E., Andrus, C. J., \& Middleton, K. M. (2013). Comparative
anatomy of flight and contour feathers in aquatic birds. \emph{Integr.
Comp. Biol.}, \emph{53}, e304.

\leavevmode\hypertarget{ref-middleton_energy_2013}{}%
Middleton, K. M., \& Coats, B. R. (2013). Energy metabolism of small
muscle phenotype mice compared to inbred strains in response to
exercise. \emph{Integr. Comp. Biol.}, \emph{53}, e146.

\leavevmode\hypertarget{ref-middleton_effects_2013}{}%
Middleton, K. M., Lujan, S. L., Hicks, J. W., \& Owerkowicz, T. (2013).
Effects of atmospheric oxygen on femur biomechanics in \emph{alligator
mississippiensis}. \emph{Anat. Rec.}, \emph{296}(special feature),
238--239.

\leavevmode\hypertarget{ref-tsai_anatomy_2013}{}%
Tsai, H. P., Middleton, K. M., \& Holliday, C. M. (2013). \emph{Anatomy
of saurischian hip joint soft tissues and its significance in body size
evolution}. Society of Vertebrate Paleontology 2013 Annual Meeting. Los
Angeles, CA.

\leavevmode\hypertarget{ref-clarke_bayesian_2012}{}%
Clarke, J. A., \& Middleton, K. M. (2012). \emph{Bayesian approaches to
the investigation of morphological rate heterogeneity in distinct
anatomical subregions}. Society of Vertebrate Paleontology Annual
Meeting 2012. Raleigh, NC.

\leavevmode\hypertarget{ref-coats_cross_2012}{}%
Coats, B. R., Middleton, K. M., Kelly, S. A., \& Garland, T., Jr.
(2012). Cross sectional anatomy of the femoral diaphysis in mice bred
for high levels of voluntary wheel running. \emph{FASEB J.}, \emph{26},
723.11.

\leavevmode\hypertarget{ref-lujan_effects_2012}{}%
Lujan, S. L., Owerkowicz, T., Elsey, R. M., Hicks, J. W., \& Middleton,
K. M. (2012). Effects of hypoxia on growth and biomechanics in limb
bones of \emph{alligator mississippiensis}. \emph{FASEB J.}, \emph{26},
908.4.

\leavevmode\hypertarget{ref-bradford_estimating_2011}{}%
Bradford, K. K., Clarke, J. A., \& Middleton, K. M. (2011).
\emph{Estimating bending mechanics of extant and fossil penguin contour
feathers}. Society of Vertebrate Paleontology. Las Vegas, NV.

\leavevmode\hypertarget{ref-coats_cross_2011}{}%
Coats, B. R., Middleton, K. M., Kelly, S. A., \& Garland, T. (2011).
Cross-sectional limb bone geometry in mice bred for high levels of
voluntary wheel running. \emph{Integr. Comp. Biol.},
\emph{51}(supplement 1), e176.

\leavevmode\hypertarget{ref-english_phylogenetic_2011}{}%
English, L. T., \& Middleton, K. M. (2011). \emph{Phylogenetic patterns
of pterosaur wing skeleton allometry}. Society of Vertebrate
Paleontology 2011 Annual Meeting. Las Vegas, NV.

\leavevmode\hypertarget{ref-lujan_hypoxia_2011}{}%
Lujan, S. L., Middleton, K. M., Owerkowicz, T., Elsey, R. M., \& Hicks,
J. W. (2011). \emph{Hypoxia-induced alterations in limb bone growth and
geometry in \textup{alligator mississippiensis}}. Society for
Integrative and Comparative Biology. Salt Lake City.

\leavevmode\hypertarget{ref-wallace_genetic_2011}{}%
Wallace, I. J., Garland, T., Jr., Wallace, S. A., Middleton, K. M.,
Kelly, S. A., Judex, S., \& Demes, B. (2011). Genetic and epigenetic
effects on diaphyseal morphology in selectively bred mice with the
mini-muscle allele. \emph{Integr. Comp. Biol.}, \emph{51}, e263.

\leavevmode\hypertarget{ref-keeney_sex_2010}{}%
Keeney, B. K., Meek, T. H., Middleton, K. M., Holness, L., Gerdeman, G.
L., Raichlen, D. A., \& Garland, T., Jr. (2010). Sex-specific
involvement of the CB1 receptor in the high voluntary wheel running of
selectively bred mice. \emph{Integr. Comp. Biol.}, \emph{50}(supplement
1), e88.

\leavevmode\hypertarget{ref-owerkowicz_atmospheric_2010}{}%
Owerkowicz, T., Andrade, F., Elsey, R. M., Middleton, K. M., \& Hicks,
J. W. (2010). Atmospheric hypoxia increases bone robusticity in the
american alligator. \emph{J. Vert. Paleontol.}, \emph{28}(3), 142A.

\leavevmode\hypertarget{ref-riskin_how_2010}{}%
Riskin, D. K., Iriarte-Díaz, J., Middleton, K. M., Breuer, K. S., \&
Swartz, S. M. (2010). How do bats accelerate? \emph{Integr. Comp.
Biol.}, \emph{50}(supplement 1), e147.

\leavevmode\hypertarget{ref-wallace_activity_2010}{}%
Wallace, I. J., Middleton, K. M., Lublinsky, S., Kelly, S. A., Judex,
S., Garland, T., Jr, \& Demes, B. (2010). \emph{Activity, genes, and
diaphyseal structure}. American Association of Physical Anthropology.

\leavevmode\hypertarget{ref-middleton_variation_2009}{}%
Middleton, K. M., Conners, M. G., \& Swartz, S. M. (2009). Variation in
rachis cross-sectional geometry within and among feathers in the barn
owl (\emph{tyto alba}). \emph{Integr. Comp. Biol.}, \emph{49}(supplement
1), e273.

\leavevmode\hypertarget{ref-swartz_scaling_2009}{}%
Swartz, S. M., Riskin, D. K., Iriarte-Díaz, J., Middleton, K. M., \&
Breuer, K. S. (2009). Scaling of flight characteristics in bats.
\emph{Integr. Comp. Biol.}, \emph{49}(supplement 1), e166.

\leavevmode\hypertarget{ref-clarke_quantitative_2007}{}%
Clarke, J. A., \& Middleton, K. M. (2007). Quantitative approaches to
the study of morphological evolution using discrete characters and a
bayesian phylogenetic approach to investigating mosaicism in avialan
evolution. \emph{J. Vert. Paleontol.}, \emph{27}(3), 59A.

\leavevmode\hypertarget{ref-gatesy_exploring_2007}{}%
Gatesy, S. M., \& Middleton, K. M. (2007). Exploring footprint
morphospace by 3-D computer-animated track simulation. \emph{J. Vert.
Paleontol.}, \emph{27}(3), 80A.

\leavevmode\hypertarget{ref-hannon_phenotypic_2007}{}%
Hannon, R. M., Kelly, S. A., Middleton, K. M., Kolb, E. M., Pomp, D., \&
Garland, T., Jr. (2007). Phenotypic effects of the ``mini-muscle''
allele in a large HR X C57Bl/6J backcross. \emph{Int Mouse Genome Conf},
\emph{S1-S4}, 185.

\leavevmode\hypertarget{ref-middleton_bone_2007}{}%
Middleton, K. M., Kelly, S. A., \& Garland, T., Jr. (2007). Bone to run:
Selective breeding and skeletal response to high voluntary activity in
mice. \emph{Integr. Comp. Biol.}, \emph{47}(supplement 1), e82.

\leavevmode\hypertarget{ref-hannon_phenotypic_2006}{}%
Hannon, R. M., Kelly, S. A., Middleton, K. M., Kolb, E. M., Pomp, D., \&
Garland, T., Jr. (2006). Phenotypic effects of the ``mighty
mini-muscle'' allele in a large HR X C57Bl/6J backcross. \emph{Integr.
Comp. Biol.}, \emph{46}(supplement 1), e55.

\leavevmode\hypertarget{ref-keeney_life_2006}{}%
Keeney, B. K., Malisch, J. L., Kelly, S. A., Hannon, R. M., Kolb, E. M.,
Lonquich, B. P., Middleton, K. M., \& Garland, T., Jr. (2006).
Life-history traits in house mice selectively bred for high voluntary
wheel-running activity. \emph{Integr. Comp. Biol.}, \emph{46}(supplement
1), e214.

\leavevmode\hypertarget{ref-kolb_effects_2006}{}%
Kolb, E. M., Kelly, S. A., Middleton, K. M., Sermsakdi, L. S., \&
Garland, T., Jr. (2006). Effects of experimental erythropoietin
elevation on voluntary exercise and maximal aerobic capacity in house
mice. \emph{Integr. Comp. Biol.}, \emph{46}(supplement 1), e76.

\leavevmode\hypertarget{ref-middleton_bone_2006}{}%
Middleton, K. M., Garland, T., Jr., Goldstein, B. D., Guduru, P. R.,
Kelly, S. A., \& Swartz, S. M. (2006). Within-bone variation in
stiffness measured by nanoindentation in high-running mice.
\emph{Integr. Comp. Biol.}, \emph{46}(supplement 1), e98.

\leavevmode\hypertarget{ref-swartz_unique_2006}{}%
Swartz, S. M., Galvao, R., Iriarte-Díaz, J., Israeli, E., Middleton, K.
M., Roemer, A., Tian, X., \& Breuer, K. S. (2006). Unique
characteristics of aerodynamics of bat flight: Evidence from direct
visualization of patterns of airflow in the wakes of naturally flying
bats. \emph{Integr. Comp. Biol.}, \emph{45}(6), 1080.

\leavevmode\hypertarget{ref-middleton_wing_2005}{}%
Middleton, K. M., \& Gatesy, S. M. (2005). Wing design and disparity in
flying vertebrates. \emph{Integr. Comp. Biol.}, \emph{44}(6), 605.

\leavevmode\hypertarget{ref-swartz_role_2005}{}%
Swartz, S. M., Kay, N., Middleton, K. M., \& Blume, J. A. (2005). The
role of thickness and curvature in dictating subchondral bone stresses
in mammalian joints. \emph{Integr. Comp. Biol.}, \emph{44}(6), 649.

\leavevmode\hypertarget{ref-swartz_can_2005}{}%
Swartz, S. M., Middleton, K. M., Iriarte-Díaz, J., Lee, M.-M., Wofford,
J. M., Breuer, K. S., \& Ritter, D. A. (2005). Can bats actively control
the mechanical properties of the wing membrane? \emph{Integr. Comp.
Biol.}, \emph{44}(6), 751.

\leavevmode\hypertarget{ref-middleton_reconstructing_2004}{}%
Middleton, K. M., \& Gatesy, S. M. (2004). Reconstructing leg function
from osteology in mesozoic birds. \emph{J. Morphol.}, \emph{260}(3),
313.

\leavevmode\hypertarget{ref-gatesy_skin_2003}{}%
Gatesy, S. M., Kenny, K. S., Middleton, K. M., Jenkins, F. A., Jr., \&
Shubin, N. H. (2003). Skin impression microtopography in triassic
theropod tracks. \emph{J. Vert. Paleontol.}, \emph{23}(3), 54A.

\leavevmode\hypertarget{ref-middleton_evolution_2002}{}%
Middleton, K. M. (2002). Evolution of the perching foot in theropods.
\emph{J. Vert. Paleontol.}, \emph{22}(3), 88A.

\leavevmode\hypertarget{ref-middleton_comparative_2000}{}%
Middleton, K. M. (2000). Comparative morphology and evolution of the
hallux in extant and fossil birds. \emph{Vert PalAsiatica},
\emph{38}(supplement), 20.

\leavevmode\hypertarget{ref-middleton_influence_2000}{}%
Middleton, K. M. (2000). Influence of hallucal reversion on terrestrial
locomotion in birds. \emph{Am. Zool.}, \emph{40}(5), 303A.

\leavevmode\hypertarget{ref-middleton_morphological_1999}{}%
Middleton, K. M. (1999). Morphological basis for hallucal orientation in
fossil birds. \emph{J. Vert. Paleontol.}, \emph{19}(3), 64A.

\leavevmode\hypertarget{ref-middleton_osteology_1999}{}%
Middleton, K. M. (1999). Osteology and evolution of the avian reversed
hallux. \emph{Am. Zool.}, \emph{39}(5), 17A.

\leavevmode\hypertarget{ref-gatesy_reconstructing_1998}{}%
Gatesy, S. M., \& Middleton, K. M. (1998). Reconstructing theropod foot
function using 3-D computer-animated track simulation. \emph{J. Vert.
Paleontol.}, \emph{18}(3), 45A.

\leavevmode\hypertarget{ref-middleton_evolution_1998}{}%
Middleton, K. M., \& Gatesy, S. M. (1998). The evolution of theropod
forelimb design and function. \emph{Am. Zool.}, \emph{37}(5), 58A.

\leavevmode\hypertarget{ref-middleton_theropod_1998}{}%
Middleton, K. M., \& Gatesy, S. M. (1998). Theropod forelimb disparity
and functional evolution. \emph{J. Vert. Paleontol.}, \emph{18}(3), 63A.

\leavevmode\hypertarget{ref-gatesy_sinking_1996}{}%
Gatesy, S. M., \& Middleton, K. M. (1996). Sinking dinosaurs:
Sub-surface preservation of foot kinematics in greenlandic theropods.
\emph{J. Vert. Paleontol.}, \emph{16}(3), 37A.

\leavevmode\hypertarget{ref-gatesy_sinking_1995}{}%
Gatesy, S. M., \& Middleton, K. M. (1995). Sinking dinosaurs:
Sub-surface foot kinematics in greenlandic theropods. \emph{Am. Zool.},
\emph{35}(5), 120A.

\endgroup

\hypertarget{other-presentations}{%
\subsection{Other Presentations}\label{other-presentations}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_other}{}
\leavevmode\hypertarget{ref-Holliday2018-ei}{}%
Holliday, C. M., Hill, C. A., Middleton, K. M., Knocke, M., \& MU
Integrative Anatomy. (2018). \emph{Inside dinosaurs: A broader impacts
program for research, teaching and public education through using
biology, physics \& evolution}. University of Missouri Medical Education
Research Day.

\leavevmode\hypertarget{ref-Johnson2018-mb}{}%
Johnson, L. E., Aldridge, K., Hill, C. A., Holliday, C. M., Middleton,
K. M., Nesbitt, A., Sherwood, R. J., \& Ward, C. V. (2018).
\emph{Integrating patient-based learning into the anatomy lab: Design
and implementation of a new multi-use anatomy facility}. University of
Missouri Medical Education Research Day.

\leavevmode\hypertarget{ref-Middleton2018-rt}{}%
Middleton, K. M., Rahman, A. J., Smolinsky, A. N., Bivens, N. J.,
Bottoms, C. A., Givens, S. A., \& King, E. G. (2018). \emph{Differential
gene expression in mouse long bones and marrow in response to three
forms of mechanical loading}. University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-Peacock2018-hs}{}%
Peacock, S. J., \& Middleton, K. M. (2018). \emph{Effects of nocturnal
blue light exposure on physiology and skeletal morphology in two strains
of mice}. University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-Smith2018-ms}{}%
Smith, C. J., Middleton, K. M., Bailleul, A. M., \& Holliday, C. M.
(2018). \emph{Bending properties of the lower temporal bar in ducks and
its significance for cranial biomechanics}. University of Missouri Life
Sciences Week.

\leavevmode\hypertarget{ref-Smolinsky2018-st}{}%
Smolinsky, A. N., Aldridge, K., \& Middleton, K. M. (2018).
\emph{Muscle-intensive and High-Impact exercises differentially
influence whole bone 3D morphology in young outbred male mice}.
University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-Ward2018-ix}{}%
Ward, C. V., Aldridge, K., Hill, C. A., Holliday, C. M., Johnson, L.,
Middleton, K. M., \& Sherwood, R. (2018). \emph{10 years of active
learning in the anatomy curriculum}. University of Missouri Medical
Education Research Day.

\leavevmode\hypertarget{ref-Cost2017-qq}{}%
Cost, I. N., Middleton, K. M., Witmer, L. M., Echols, M. S., \&
Holliday, C. M. (2017). \emph{Biomechanics of the feeding apparatus of
parrots (aves: Psittaciformes)}. University of Missouri Life Sciences
Week.

\leavevmode\hypertarget{ref-Hill2017-jr}{}%
Hill, C. A., Aldridge, K., Holliday, C. M., Johnson, L., Middleton, K.
M., Sherwood, R., \& Ward, C. V. (2017). \emph{Approaches for active
learning in a flipped undergraduate health sciences anatomy classroom}.
University of Missouri School of Medicine Health Sciences Research Day.

\leavevmode\hypertarget{ref-Holliday2017-xi}{}%
Holliday, C. M., Hill, C. A., Davis, J. L., Witmer, L. M., \& Middleton,
K. M. (2017). \emph{Inside dinosaurs: A broader impacts program for
research, teaching and public education through dinosaur biology,
physics and evolution}. University of Missouri School of Medicine Health
Sciences Research Day.

\leavevmode\hypertarget{ref-Ngoma2017-oq}{}%
Ng'oma, E., Perinchery, A., Middleton, K. M., \& King, E. G. (2017).
\emph{Coordination of resource availability with allocation in a
synthetic population: Lifespan and its heritability across dietary
regimes}. 58th Annual Drosophila Research Conference.

\leavevmode\hypertarget{ref-Ngoma2017-vs}{}%
Ng'oma, E., Perinchery, A., Middleton, K. M., \& King, E. G. (2017).
\emph{Coordination of resource availability with allocation in a
synthetic population: Lifespan and its heritability across dietary
regimes}. University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-Ngoma2017-ck}{}%
Ng'oma, E., Perinchery, A., Middleton, K. M., \& King, E. G. (2017).
\emph{Evolutionary potential of nutrition-dependent effects on lifespan
in a multi-parental population of \textup{drosophila melanogaster}}.
Evolution 2017.

\leavevmode\hypertarget{ref-Peacock2017-ep}{}%
Peacock, S. J., Bates, K. A., Talton, O. O., Schulz, L. C., \&
Middleton, K. M. (2017). \emph{Effects of perinatal circadian
programming on activity and skeletal morphology in C57BL/6 mice}.
University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-Sellers2017-nv}{}%
Sellers, K. C., Middleton, K. M., Davis, J. L., \& Holliday, C. M.
(2017). \emph{Biomechanics and the evolution of the crocodyliform
skull}. University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-Smith2017-io}{}%
Smith, C. J., Holliday, C. M., Middleton, K. M., \& Bailleul, A. M.
(2017). \emph{Bending properties of the jugal bone in mallard ducks and
its significance for cranial biomechanics}. University of Missouri Life
Sciences Week.

\leavevmode\hypertarget{ref-Smolinsky2017-fj}{}%
Smolinsky, A. N., \& Middleton, K. M. (2017). \emph{Comparing femur
cross-sectional morphology in young outbred mice following daily
exposure to muscle-, impact-, or combined loading of the hind limb
skeleton}. University of Missouri Life Science Week.

\leavevmode\hypertarget{ref-Smolinsky2017-ht}{}%
Smolinsky, A. N., \& Middleton, K. M. (2017). \emph{The effects of
muscle- and impact-dominated loading on femoral cross-section morphology
and mineral apposition in young outbred mice}. University of Missouri
Life Sciences Week.

\leavevmode\hypertarget{ref-Ward2017-jh}{}%
Ward, C. V., Aldridge, K., Hill, C. A., Holliday, C. M., Johnson, L.,
Middleton, K. M., \& Sherwood, R. (2017). \emph{10 years of active
learning in the anatomy curriculum}. University of Missouri School of
Medicine Health Sciences Research Day.

\leavevmode\hypertarget{ref-Wilkin2017-md}{}%
Wilkin, A. T., Middleton, K. M., Sellers, K. C., Cost, I. N., Davis, J.
L., \& Holliday, C. M. (2017). \emph{Modeling complex cranial joints in
\textup{varanus exanthematicus}}. University of Missouri Life Sciences
Week.

\leavevmode\hypertarget{ref-cooper_impact_2016}{}%
Cooper, J., Herbst, E., Sellers, K. C., Cost, I. N., Davis, J. L.,
Middleton, K. M., \& Holliday, C. M. (2016). \emph{The impact of muscle
anatomy on skull loading in hard-biting animals}. University of Missouri
Summer 2016 Undergraduate Research and Creative Achievements Forum.

\leavevmode\hypertarget{ref-herbst_3d_2016}{}%
Herbst, E., Cooper, J., Cost, I. N., Sellers, K. C., Middleton, K. M.,
\& Holliday, C. M. (2016). \emph{3D reconstruction of the feeding
biomechanics of the north american aetosaur \textup{desmatosuchus}}.
University of Missouri Summer 2016 Undergraduate Research and Creative
Achievements Forum.

\leavevmode\hypertarget{ref-Peacock2016-cs}{}%
Peacock, S. J., Coats, B. R., Kirkland, J. K., Tanner, C. A., Garland,
T., Jr., \& Middleton, K. M. (2016). \emph{History of exercise,
cross-sectional geometry, and bending mechanics: Inferences based on
three strains of mice}. University of Missouri Health Science Research
Day.

\leavevmode\hypertarget{ref-peacock_predicting_2016}{}%
Peacock, S. J., \& Middleton, K. M. (2016). \emph{Predicting the bending
properties of long bones: Insights from an experimental mouse model}.
University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-Sellers2016-vb}{}%
Sellers, K. C., Davis, J. L., Middleton, K. M., \& Holliday, C. M.
(2016). \emph{A high-fidelity, 3D model of the skull of
\textup{alligator mississippiensis} (archosauria: Crocodylia) and its
significance for vertebrate feeding biomechanics}. University of
Missouri Health Sciences Research Day.

\leavevmode\hypertarget{ref-Smolinsky2016-ox}{}%
Smolinsky, A. N., \& Middleton, K. M. (2016). \emph{Comparison of impact
loading and wheel running on femoral cross-section morphology and growth
in young outbred mice}. University of Missouri Health Science Research
Day.

\leavevmode\hypertarget{ref-smolinsky_comparison_2016a}{}%
Smolinsky, A. N., \& Middleton, K. M. (2016). \emph{Comparison of impact
loading and wheel running on femoral cross-section morphology and growth
in young outbred mice}. University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-bira_inexpensive_2015}{}%
Bira, N. P., \& Middleton, K. M. (2015). \emph{Inexpensive study of
small animal locomotion through indirect scientific rotoscoping}.
University of Missouri Spring 2015 Undergraduate Research and Creative
Achievements Forum.

\leavevmode\hypertarget{ref-kirkland_effects_2015}{}%
Kirkland, J. K., Peacock, S. J., Coats, B. R., \& Middleton, K. M.
(2015). \emph{Effects of cross sectional area on bone strength in three
strains of mice}. University of Missouri Summer 2015 Undergraduate
Research and Creative Achievements Forum.

\leavevmode\hypertarget{ref-kirkland_effects_2015a}{}%
Kirkland, J. K., Peacock, S. J., Coats, B. R., \& Middleton, K. M.
(2015). \emph{Effects of cross sectional area on bone strength in three
strains of mice}. ABRCMS. Seattle, WA.

\leavevmode\hypertarget{ref-rashid_axial_2015}{}%
Rashid, I. S., Carter, P. A., Garland, T., Jr., \& Middleton, K. M.
(2015). \emph{Axial loading of caudal and lumbar vertebrae of selected
high running lines of mice with different exercise regimens}. University
of Missouri Summer 2015 Undergraduate Research and Creative Achievements
Forum.

\leavevmode\hypertarget{ref-smolinsky_fracture_2015}{}%
Smolinsky, A. N., Pfeiffer, F., Middleton, K. M., \& Holliday, C. M.
(2015). \emph{Fracture mechanics of the mandible in \textup{alligator
mississippiensis}}. University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-tsai_hip_2015}{}%
Tsai, H. P., Middleton, K. M., \& Holliday, C. M. (2015). \emph{The hip
joint functional module and its significance in the evolution of avian
locomotor posture}. University of Missouri Life Sciences Week.

\leavevmode\hypertarget{ref-bira_development_2014}{}%
Bira, N. P., \& Middleton, K. M. (2014). \emph{Development of an
inexpensive method for studying small animal locomotion through indirect
scientific rotoscoping}. University of Missouri Summer 2014
Undergraduate Research and Creative Achievements Forum.

\leavevmode\hypertarget{ref-casey_estimating_2014}{}%
Casey, T. K., \& Middleton, K. M. (2014). \emph{Estimating comparative
bending properties of feather rachises in four species of birds}.
University of Missouri Summer 2014 Undergraduate Research and Creative
Achievements Forum.

\leavevmode\hypertarget{ref-cheney_wing_2014}{}%
Cheney, J. A., Konow, N., Middleton, K. M., Breuer, K. S., Roberts, T.
J., Giblin, E. L., \& Swartz, S. M. (2014). \emph{Wing membrane muscle
activity in bats}. North American Society for Bat Research. Albany, NY.

\leavevmode\hypertarget{ref-peacock_minimsc_2014}{}%
Peacock, S. J., Coats, B. R., Tanner, C. A., \& Middleton, K. M. (2014).
\emph{\textup{Minimsc} genotype increases resistance to bending in mouse
femora}. MU Life Sciences Week 2014.

\leavevmode\hypertarget{ref-holliday_12_2013}{}%
Holliday, C. M., Knocke, M., Cowgill, L. W., Middleton, K. M., Woods,
A., Maddux, S. D., Ward, C. V., Dufeau, D. L., Warren, A. L., George, I.
D., Moffett, E. A., Tsai, H. P., Savage, C. R., Swartz, S., Lo Presti,
E. J., Munds, R. A., Hammond, A. S., Sellers, K. C., Gant, C. A., \&
Winkler, Z. J. (2013). \emph{K-12 and community outreach using
interactive and experiential anatomical learning: Dinosaurs \& cavemen}.
MU School of Medicine Medical Education Day.

\leavevmode\hypertarget{ref-middleton_physiology_2013}{}%
Middleton, K. M. (2013). \emph{The physiology, function, and evolution
of vertebrate locomotor tissues}. University of Missouri Life Sciences
Week.

\leavevmode\hypertarget{ref-salas_effects_2013}{}%
Salas, D. L., Coats, B. R., Kelly, S. A., Garland, T., Jr, \& Middleton,
K. M. (2013). \emph{Effects of genetics and exercise on mid-femoral
diaphyseal mineral apposition in mice}. University of Missouri Summer
2013 Undergraduate Research and Creative Achievements Forum.

\leavevmode\hypertarget{ref-riskin_how_2010a}{}%
Riskin, D. K., Iriarte-Díaz, J., Middleton, K. M., Breuer, K. S., \&
Swartz, S. M. (2010). \emph{How do bats modulate thrust and lift
production during flight?} North American Symposium on Bat Research.

\leavevmode\hypertarget{ref-riskin_effects_2008}{}%
Riskin, D. K., Iriarte-Díaz, J., Middleton, K. M., Breuer, K. S., \&
Swartz, S. M. (2008). \emph{Effects of body size on the wing kinematics
of bats}. Society for Experimental Biology Annual Meeting. Marseille,
France.

\leavevmode\hypertarget{ref-bahlman_flying_2007}{}%
Bahlman, J. W., Riskin, D. K., Middleton, K. M., Iriarte-Díaz, J., \&
Swartz, S. M. (2007). \emph{Flying squirrels don't glide steady:
Implications for bat evolution}. North American Symposium on Bat
Research.

\leavevmode\hypertarget{ref-middleton_material_2007}{}%
Middleton, K. M., Swartz, S. M., Kovnats, J. M., Lee, M.-M., \& McComas,
K. M. (2007). \emph{Material properties of bat wing bones estimated by
cantilever bending}. North American Symposium on Bat Research.

\leavevmode\hypertarget{ref-swartz_unique_2005}{}%
Swartz, S. M., Galvao, R., Iriarte-Díaz, J., Israeli, E., Middleton, K.
M., Roemer, A., Sullivan, A., Tian, X., \& Breuer, K. S. (2005).
\emph{Unique characteristics of aerodynamics of bat flight: Evidence
from direct visualization of patterns of airflow in the wakes of
naturally flying bats}. North American Symposium on Bat Research.

\endgroup

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\hypertarget{university-of-missouri}{%
\subsection{University of Missouri}\label{university-of-missouri}}

\LTXtable{\textwidth}{teaching.tex}

\hypertarget{california-state-university-san-bernardino}{%
\subsection{California State University, San
Bernardino}\label{california-state-university-san-bernardino}}

\begin{tabular}{ll}
  2007-2011 & Biology of the Chordates \\ 
  2008-2012 & Human Physiology and Anatomy \\ 
  2010-2012 & Biostatistics \\ 
  2008, 2010, 2012 & Graduate Seminar \\ 
  2008-2011 & Biology Seminar \\ 
  2008 & Advanced Vertebrate Morphology \\ 
  \end{tabular}

\hypertarget{invited-seminars}{%
\section{Invited Seminars}\label{invited-seminars}}

\begin{tabular}{ll}
  2001 & University of Chicago \\ 
  2001 & American Museum of Natural History \\ 
  2007 & CSU, San Bernardino \\ 
  2007 & University of California, Riverside \\ 
  2007 & CSU, Fullerton \\ 
  2007 & Loma Linda University \\ 
  2010 & Grove High School, Redlands, CA \\ 
  2010 & CSU, Northridge \\ 
  2011 & University of Missouri \\ 
  2012 & La Sierra College \\ 
  2012 & Grinnell College \\ 
  2013 & MU Evolutionary Studies EvoBlitz \\ 
  2013 & University of Texas at Austin \\ 
  2013 & Saint Louis University \\ 
  2013 & MU Division of Biological Sciences \\ 
  2014 & Northeast Ohio Medical University \\ 
  2014 & MU Math in Life Sciences Freshman Interest Group \\ 
  2014 & MU LSUROP Evening Seminar Speaker \\ 
  2017 & MU Saturday Morning Science \\ 
  2018 & MU Department of Pathology and Anatomical Sciences \\ 
  \end{tabular}

\hypertarget{professional-service}{%
\section{Professional Service}\label{professional-service}}

\hypertarget{referee}{%
\subsection{Referee}\label{referee}}

\begin{itemize}
\tightlist
\item
  Acta Anatomica
\item
  Acta Palaeontologica Polonica
\item
  Acta Zoologica Sinica
\item
  Ameghiniana
\item
  American Journal of Physical Anthropology
\item
  Anatomical Record
\item
  Biology Letters
\item
  Comparative Biochemistry and Physiology
\item
  Current Biology
\item
  Evolution
\item
  IEEE Visualization \& Graphics
\item
  Integrative Organismal Biology
\item
  International Journal of Primatology
\item
  Journal of Anatomy
\item
  Journal of Morphology
\item
  Journal of Vertebrate Paleontology
\item
  Journal of Zoology
\item
  Nature
\item
  Nature Communications
\item
  Naturwissenschaften
\item
  Palaeontology
\item
  Paleobiology
\item
  Paleobios
\item
  PeerJ
\item
  PLoS One
\item
  Proceedings of the National Academy of Sciences USA
\item
  Proceedings of the Royal Society (Biological Sciences)
\item
  Quarterly Review of Biology
\item
  Restoration Ecology
\item
  Royal Society Open Science
\item
  Zoological Journal of the Linnean Society
\item
  Zoology
\end{itemize}

\hypertarget{nsf-panel-service}{%
\subsection{NSF Panel Service}\label{nsf-panel-service}}

\begin{tabular}{ll}
  2012 & Division of Evolutionary Biology -- Systematics and Biodiversity Science \\ 
  \end{tabular}

\hypertarget{nsf-ad-hoc-reviewer}{%
\subsection{NSF Ad Hoc Reviewer}\label{nsf-ad-hoc-reviewer}}

\begin{tabular}{ll}
  2009 & National Science Foundation -- IOB \\ 
  2010 & National Science Foundation -- DEB \\ 
  2012 & National Science Foundation -- IOB \\ 
  2017 & National Science Foundation -- IOB \\ 
  2019 & National Science Foundation -- IOB \\ 
  \end{tabular}

\hypertarget{university-of-missouri-research-board}{%
\subsection{University of Missouri Research
Board}\label{university-of-missouri-research-board}}

\begin{tabular}{ll}
  2015 & Ad hoc reviewer \\ 
  \end{tabular}

\hypertarget{reviewer-textbooks}{%
\subsection{Reviewer (Textbooks)}\label{reviewer-textbooks}}

\begin{tabular}{lll}
  2003 & Miller, KR and JS Levine. Biology & Pearson-Prentice Hall \\ 
  2010 & Tate, P. Anatomy and Physiology & McGraw Hill \\ 
  2010 & Biological Sciences Curriculum Studies. BSCS Biology: A Human Approach. 4th Ed. & Kendall Hunt Publishing \\ 
  \end{tabular}

\hypertarget{reviewer-for-deutsche-forschungsgemeinschaft-german-research-foundation}{%
\subsection{Reviewer for Deutsche Forschungsgemeinschaft (German
Research
Foundation)}\label{reviewer-for-deutsche-forschungsgemeinschaft-german-research-foundation}}

\begin{tabular}{ll}
  2018 & Life Sciences 1: Molecular and Organismic Biology \\ 
  \end{tabular}

\hypertarget{department-and-university-service}{%
\section{Department and University
Service}\label{department-and-university-service}}

\hypertarget{current-1}{%
\subsection{Current}\label{current-1}}

\begin{tabular}{ll}
  2020-Present & PAS Director of Graduate Studies \\ 
  2020-Present & School of Medicine Block 4 Planning Committee \\ 
  2018-Present & MU School of Medicine Faculty Committee for Diversity and Inclusion \\ 
  2015-Present & School of Medicine Advice Support and Career (ASC) Preclerkship Advisor \\ 
  2014-Present & School of Medicine eResources Committee \\ 
  2012-Present & MU Doctoral Faculty \\ 
  2012-Present & MU Graduate Faculty \\ 
  2012-Present & Pathobiology Area Program Faculty \\ 
  \end{tabular}

\hypertarget{past-1}{%
\subsection{Past}\label{past-1}}

\textbf{University of Missouri}

\begin{tabular}{ll}
  2014-2019 & School of Medicine Block 2 Planning Committee \\ 
  2013-2019 & PAS Promotion and Tenure Committee \\ 
  2013-2020 & PAS Director of Admissions \\ 
  2016-2019 & Evolution and Social Science Group (ESS) steering committee \\ 
  2016-2019 & MU School of Medicine Admissions Committee \\ 
  2016-2019 & MU Information Technology Committee \\ 
  2016-2018 & MU Library Committee \\ 
  2016 & Chair, MU Life Sciences Week Genetics, Evolution, and Environment Poster Competition \\ 
  2016 & MU Office of Undergraduate Research focus group \\ 
  2015 & Life Sciences Undergraduate Research Opportunity Program Selection Committee \\ 
  2014-2018 & MU Life Sciences Week poster competition judge \\ 
  2013-2017 & PAS Director of Graduate Studies \\ 
  2013-2016, 2019 & SOM Summer Research Internship in Medical Sciences Selection Committee \\ 
  2013, 2015-2019 & PAS Assistant Teaching Professor Search Committee \\ 
  2013-2019 & PAS Lecturer Search Committee \\ 
  2013-2014 & School of Medicine Block 4 Planning Committee \\ 
  \end{tabular}

\textbf{California State University, San Bernardino}

\begin{tabular}{ll}
  2009-2012 & Institutional Animal Care and Use Committee \\ 
  2008-2012 & NSF Mathematics and Science Scholars Mentor \\ 
  2007-2012 & Pre-Dental Club Faculty Advisor \\ 
  2007-2012 & Health Professions Advisory Committee \\ 
  2007-2012 & Biology Department Webmaster \\ 
  2009 & College of Natural Sciences Outstanding Students Evaluation Committee \\ 
  \end{tabular}

\hypertarget{professional-organizations}{%
\section{Professional Organizations}\label{professional-organizations}}

\begin{itemize}
\tightlist
\item
  American Association of Anatomists
\item
  International Association of Dental Research
\item
  International Society of Vertebrate Morphology
\item
  Society of Avian Paleontology and Evolution
\item
  Society of Integrative and Comparative Biology
\item
  Society of Vertebrate Paleontology
\end{itemize}

\hypertarget{televised-outreach}{%
\section{Televised Outreach}\label{televised-outreach}}

\LTXtable{\textwidth}{televised.tex}

\end{document}
