---
name: Kevin Middleton, Ph.D.
position: |
  | Associate Professor
  | Department of Pathology & Anatomical Sciences
  | University of Missouri School of Medicine
address: |
  | 1 Hospital Dr., Medical Science Building M263
  | Columbia, MO 65212
www: middletonlab.org
email: "middletonk@missouri.edu"
phone: "573 884 3192"
pubmed: kevin.middleton.1
orcid: 0000-0003-4704-1064
github: kmiddleton
scholar: Ziha7x8AAAAJ
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
headcolor: "000090"
papersize: letterpaper
---

\renewcommand{\labelitemi}{\textbullet}

```{r setup, include=FALSE}
#remotes::install_github("kmiddleton/vitae")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)

include_refs <- TRUE
```

# Professional Experience

```{r, echo=FALSE}
tribble(
  ~ Position, ~ University, ~ Location, ~ Dates,
  "Associate Professor, Department of Pathology & Anatomical Sciences", "University of Missouri", "Columbia, MO", "2012 - Present",
  "Assistant to Associate Professor, Department of Biology", "CSU San Bernardino", "San Bernardino, CA", "2007 - 2012",
  "NIH NRSA Postdoctoral Fellow", "Brown University and University of California, Riverside", "Providence, RI and Riverside, CA", "2005 - 2007",
  "Postdoctoral Research Associate, Department of Ecology and Evolutionary Biology", "Brown University", "Providence, RI", "2003 - 2005"
) %>% 
  detailed_entries(what = Position, when = Dates,
                   where = University, with = Location)
```

# Education

```{r, echo=FALSE}
tribble(
  ~ Degree, ~ University, ~ Location, ~ Dates,
  "PhD Ecology and Evolutionary Biology", "Brown University", "Providence, RI", "1996 - 2003",
  "BS Biology, Summa Cum Laude", "Wake Forest University", "Winston-Salem, NC", "1992 - 1995"
) %>% 
  detailed_entries(when = Dates, what = University,
                   where = Degree, with = Location)
```


# Research Interests and Current Projects

My overall research focuses on form, physiology, and function of the skeletal and muscular systems in the contexts of growth, locomotion, feeding, and evolution. In my work, I integrate studies across multiple scales from micro-scale structural materials of bone to macro-scale whole bone and multi-element cranial morphology to evolutionary changes across taxa and with comparisons to extinct organisms.

## Development of Bayesian and machine learning models for the prediction of craniofacial growth in humans.

- For orthodontic and craniofacial interventions, estimation of the timing of peak growth and/or the amount of remaining growth is is important for planning treatment. We are seeking to estimate these quantities for a wide range of traits in two- and three-dimensional imaging.

## Evolution of the reptile head: integrating cranial biomechanics, muscle modeling, and brain evolution to understand cranial kinesis and diversity

- Computational modelling of cranial function has allowed us to estimate all the forces acting on the jaws and skull. We are developing techniques to apply contrast-enhanced imaging to refine muscle force estimates and generate a complete picture of head function.

## Effects of exercise and genetic background on skeletal form, physiology, and biomechanics using high activity mice as a model organism

- Although "exercise builds strong bones", genetics play a large part in bone's response to exercise. I have developed an animal model to investigate the relative roles of these two key determinants of skeletal form. 


# Awards

```{r awards, results="asis"}
tribble(
  ~ Year, ~ Award,
  2019, "Gold Chalk Award for Graduate Teaching",
  2017, "School of Medicine Award for Outstanding Preclinical Faculty Education",
  2017, "Ann K. Covington Award for Undergraduate Mentoring"
) %>%
  detailed_entries(when = Year, what = Award)
```


# Grants in Preparation

```{r}
tribble(~ Dates, ~ Title, ~ Agency, ~ PIs,
        "2021", 
        "R01 - Maturation-based Prediction of Craniofacial Growth",
        "NIH NIDCR",
        "RJ Sherwood and D Duren (Multiple PI) \\\\ \\textbf{Kevin M Middleton} co-I (Lead data scientist; 10\\% salary support)",
        
        "2021",
        "R01 - Craniofacial Growth Prediction in Diﬀerent Facial Types",
        "NIH NIDCR",
        "RJ Sherwood and HS Oh (Multiple PI) \\\\ \\textbf{Kevin Middleton} co-I (Lead data scientist; 10\\% salary support)",
        
        "2021",
        "R01 - Connecting the Genome to Structure and Function of Wing Morphology and Flight Performance in \\emph{Drosophila}",
        "NIH NIGMS",
        "Elizabeth King and \\textbf{Kevin Middleton} (Multiple PI)") %>% 
  detailed_entries(when = Dates, what = Title, with = Agency,
                   where = PIs, .protect = FALSE)
```


<!--
# Grants in Review

-->


# Current Support

```{r}
tribble(~ Dates, ~ Title, ~ Agency, ~ PIs, ~ Notes,
        "2021-2023", 
        "Maturation-based prediction of craniofacial growth",
        "University of Missouri TRIUMPH",
        "RJ Sherwood and D Duren (Multiple PI) \\\\ \\textbf{Kevin Middleton}: co-Investigator (5\\% salary support)",
        "This project leverages the considerable resources from the parent project to create Bayesian models of craniofacial growth timing and use machine learning approaches to accurately predict facial growth parameters. (\\$100,000)",
        
        "2015--2022",
        "R01 - Craniofacial Growth Prediction in Diﬀerent Facial Types",
        "NIH NIDCR",
        "RJ Sherwood and HS Oh (Multiple PI) \\\\ \\textbf{Kevin Middleton} co-I (Lead data scientist; 10\\% salary support)",
        "We have identified landmarks on over 25,000 lateral cephalographs from 5,247 individuals age 0-27 years from eight growth studies. This research will 1) estimate population- and individual-level timing of pubertal growth and adult size for multiple craniofacial traits, 2) provide diagnostic reference charts for craniofacial measures, 3) develop prognostic tools to predict remaining growth/change and the timing of the pubertal growth spurt for craniofacial traits, 4) make these valuable resources available to clinicians and researchers via an easy-to-use free web-based application.") %>% 
  detailed_entries(when = Dates, what = Title, with = Agency,
                   where = PIs, why = Notes,
                   .protect = FALSE)
```


# Past Grants and Fellowships

```{r}
tribble(~ Dates, ~ Title, ~ Agency, ~ PIs, ~ Notes,
        "2019--2020",
        "Administrative Supplement to \\emph{Craniofacial Growth Prediction in Different Facial Types}",
        "NIH NIDCR",
        "RJ Sherwood (PI) \\\\ \\textbf{Kevin Middleton} co-I (10\\% salary support)",
        "This administrative supplement leveraged the considerable resources from the parent project to create Bayesian models of craniofacial growth timing and use machine learning approaches to accurately predict facial growth parameters.  (\\$116,169)",
        
        "2017",
        "Differential Gene Expression of Bone in Response to Experimental Loading Regimes",
        "MU DNA Core Facility NextGen Sequencing Pilot Award",
        "\\textbf{Kevin Middleton} PI",
        "This award supported preliminary research into the differential expression of genes in bone: RNA sequencing and analysis of data. (\\$10,760)",
        
        "2015--2019",
        "Collaborative Research: Dinosaur Jaw Muscle Evolution and\\\\the Origins of Avian Cranial Kinesis",
        "NSF -- Integrative Organismal Systems",
        "Casey Holliday, Lead PI, \\\\ \\textbf{Kevin Middleton}, co-PI, \\\\ Julian Davis (Sounthern Indiana University), co-PI, \\\\ Lawrence Witmer (Ohio University), co-PI",
        "This project focused on the evolution and function of intra-cranial mobility (cranial kinesis) in dinosaurs and birds. We developed novel techniques for imaging muscle structure via contrast-enhanced micro-CT, new finite-element computational models for estimating cranial loads in extant and extinct animals, and visualization techniques for representing 3D data in two-dimensional space. (\\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1457319}{NSF IOS 1457319}; \\$606,705).",
        
        "2010--2015",
        "Collaborative Research: Wings to flippers - phylogenetics, character acquisition,\\\\and feather biomechanics in the evolution of wing-propelled diving",
        "NSF -- Systematic Biology",
        "Julia Clarke (University of Texas, Austin), Lead PI \\\\ \\textbf{Kevin Middleton}, co-PI \\\\ Daniel Ksepka (North Carolina State University), co-PI",
        "The goal of this project was to integrate studies of phylogenetics, sensory systems evolution, bone microstructure, feather function, and wing biomechanics across multiple transitions from aerial ﬂight to underwater wing-propelled diving. (\\href{http://www.nsf.gov/awardsearch/showAward.do?AwardNumber=0949945}{NSF DEB 0949945}; \\$471,717).",
        
        "2009--2014",
        "Collaborative Research: LiT: Effects of environmental oxygen on growth and physiological performance in the American alligator: A case study in experimental paleophysiology",
        "NSF -- Integrative Organismal Systems",
        "James Hicks (University of California, Irvine), Lead PI \\\\ \\textbf{Kevin Middleton}, co-PI \\\\ Bryan Rourke (CSU Long Beach) , co-PI",
        "This project studied the effects of altered environmental oxygen level on alligator physiology (growth, locomotor ability, muscle and bone structure). We used a long-term experiment of raising American alligators in varying levels of atmospheric oxygen for 24 months. We found that overall growth rates as well as skeletal morphology was largely unaltered by changes in available oxygen. (\\href{http://www.nsf.gov/awardsearch/showAward.do?AwardNumber=0922576}{NSF IOS 0922576}; \\$517,931)",
        
        "2011--2014",
        "Maturation of an S-STEM scholarship program at a Hispanic,\\\\minority serving institution",
        "NSF -- Division of Undergraduate Education",
        "Kimberley Cousins, Lead PI \\\\ \\textbf{Kevin Middleton}, co-PI",
        "This project supported four years of continued funding and expansion of CSUSB Math and Science Scholars scholarship program designed to encourage minority, under-represented, and economically disadvantaged students to enter STEM disciplines. This grant was awarded while I was a faculty member at California State University San Bernardino, but I resigned as co-PI on moving to the University of Missouri. (\\href{http://www.nsf.gov/awardsearch/showAward.do?AwardNumber=1060632}{NSF DUE 1060632}; co-PI; \\$591,231)",
        
        "2008--2009",
        "Extramural Associates Research Development Award (EARDA) pilot grant:\\\\ \\emph{Establishment of an Inbred Strain of ``Mini-muscle'' Phenotype, High-activity Mice}",
        "NIH NIAMS",
        "Kevin Middleton, PI",
        "Award to establish an inbred strain of mice. (\\$15,000; sub-award from NIH 5G11HD052368-03)",
        
        "2005--2007",
        "Effects of Genetics, Exercise, and Age on Bone Mechanics",
        "NIH Ruth Kirschstein National Research Service Award",
        "Kevin Middleton, PI",
        "Postdoctoral fellowhsip (NIH 1F32AR053008-01)",
        
        "2002",
        "Honorable Mention, Alfred Sherwood Romer Prize",
        "Society of Vertebrate Paleontology",
        "",
        "Award for outstanding graduate research",
        
        "2000--2003",
        "Dissertation Improvement Grant: Evolution and Functional Morphology of the Theropod Foot",
        "NSF",
        "Kevin Middleton co-PI",
        "Grant in support of doctoral dissertation research",
        
        "1999",
        "Grant-in-Aid of Paleontological Research",
        "Paleontological Society",
        "Kevin Middleton, PI",
        "Award for Outstanding Student Scholarship Proposal",
        
        "1999",
        "Student Research Grant",
        "Geological Society of America",
        "Kevin Middleton PI",
        "Award for Exceptional Merit in Conception and Presentation",
        
        "1999",
        "Grant in Aid of Research",
        "Sigma Xi",
        "Kevin Middleton, PI",
        "Grant in support of doctoral dissertation research",
        
        "1997",
        "Honorable Mention, Graduate Research Fellowship",
        "NSF",
        "Kevin Middleton, PI",
        "Grant in support of doctoral dissertation research"
        
        ) %>% 
  detailed_entries(when = Dates, what = Title, with = Agency,
                   where = PIs, why = Notes,
                   .protect = FALSE)
```

```{r include=FALSE}
## FIXME Publications
```


# Publications

A full list of my published work can be found at: \href{https://www.ncbi.nlm.nih.gov/myncbi/kevin.middleton.1/bibliography/public/}{\color[HTML]{000090}{NIH PubMed}}


## Dissertation

```{r dissertation}
# Load bib file
bib_entries <- bibliography_entries("Paperpile.bib")

if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Dissertation"))
}
```


## Refereed Research Papers

```{r research-papers, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Papers")) %>%
    arrange(issued, author)
}
```


## Manuscripts in Review

```{r in-review, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/In review")) %>% 
    arrange(author)
}
```


## Book Chapters

```{r book-chapters, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Book chapters")) %>%
    arrange(issued, author)
}
```


## Invited Reviews

```{r invited-reviews, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Reviews")) %>%
    arrange(issued, author)
}
```


## Book Reviews

```{r book-reviews, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Book reviews")) %>%
    arrange(issued, author)
}
```


## Published Data Sets

```{r datasets, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Datasets")) %>%
    arrange(issued, author)
}
```


## Manuscripts in Preparation

```{r in-prep, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/In prep")) %>%
    arrange(author)
}
```


# Postdoctoral Supervisor

```{r postdoc}
tribble(
  ~ Dates, ~ Name, ~ Notes,
  "2015-2018", "Alida Bailleul, PhD", "Currently an Assistant Professor at the Institute of Vertebrate Paleontology and Paleoanthropology, Beijing"
) %>% 
  detailed_entries(when = Dates, what = Name, where = Notes)
```


# Graduate Advisor

```{r, grad_advisor}
tribble(
  ~ Dates, ~ Name, ~ Degree, ~ Notes,
  "2015-2019", "Sarah Peacock", "Ph.D. University of Missouri", "Currently Assistant Teaching Professor at Northeastern University",
  "2013-2018", "Amanda Smolinsky", "Ph.D. University of Missouri", "Currently an Assistant Teaching Professor at Roanoke College",
  "2011-2012", "Katherine Johnson", "M.S., CSUSB", "Completed doctoral studies at University of California, Riverside",
  "2010-2012", "Brittney Coats", "M.S., CSUSB", "Completed doctoral studies at the University of Chicago",
  "2008-2012", "Susan Lujan", "M.S., CSUSB", "Currently a lecturer at California State University, San Bernardino"
) %>% 
  detailed_entries(when = Dates, what = Name, with = Degree, where = Notes)
```


# Graduate Committee Member

## Current

```{r, current_committee}
tribble(
  ~ Dates, ~ Name, ~ Degree,
  "2021-Present", "Jeremy Webb", "M.S.; Geological Sciences",
  "2021-Present", "Wade Leibach", "M.S.; Geological Sciences",
  "2021-Present", "Delaney Ryan", "M.S.; Geological Sciences",
  "2020-Present", "Gabriel Jacobs", "Ph.D.; Geological Sciences",
  "2020-Present", "Christian Perez", "Ph.D.; Biological Sciences",
  "2019-Present", "Emily Lessner", "Ph.D.; Pathobiology",
  "2019-Present", "Samuel Sullivan", "Ph.D.; Pathobiology",
  "2019-Present", "Mikaela Pulsipher", "M.S.; Geological Sciences",
  "2018-Present", "Sean Greer", "Ph.D.; Pathobiology",
  "2016-Present", "Elizabeth Cho", "Ph.D.; Anthropology",
  "2016-Present", "Deise Cruz", "Ph.D.; Biological Sciences",
  "2015-Present", "Rob'yn Johnston", "Ph.D.; Anthropology"
) %>% 
  detailed_entries(when = Dates, what = Name, with = Degree)
```


## Past

```{r, past_committee}
tribble(
  ~ Dates, ~ Name, ~ Degree, ~ Notes,
  "2016-2021", "Kaleb Sellers", "Ph.D.; Pathobiology", "Currently postdoctoral researcher, Rocky Vista University",
  "2017-2021", "Faye McGechie", "Ph.D.; Pathobiology", "Currently postdoctoral researcher, University of Chicago",
  "2017-2020", "Rebecca Dirkes", "Ph.D.; Nutrition & Exercise Physiology", "Currently pursuing certificate in nutrition, University of Missouri",
  "2019-2020", "Alec Wilken", "M.S.; Pathology and Anatomical Sciences", "Currently doctoral student at University of Chicago",
  "2016-2020", "Melanie Boeyer", "Ph.D.; Pathobiology", "Currently postdoctoral research associate at the University of Missouri",
  "2015-2020", "Sharon Kuo", "Ph.D.; Pathobiology", "Currently postdoctoral research associate at Pennsylvania State University",
  "2018-2019", "Ellee Cook", "Ph.D.; Biological Sciences", "Currently teaching high school science",
  "2015-2019", "Ian Cost", "Ph.D.; Pathobiology", "Currently assistant professor at Albright College",
  "2017-2018", "Landry Konan", "M.S.; Pathology and Anatomical Sciences", "Fulbright Fellow",
  "2017-2018", "Stephanie Rosbach", "M.S.; Geological Sciences", "",
  "2016-2018", "Tara Selly", "Ph.D.; Geological Sciences", "Currently research assistant professor at the University of Missouri",
  "2015-2017", "Edward Ramirez", "M.S.; Biological Sciences", "",
  "2015-2017", "Steven Hanson", "Ph.D.; Pathobiology", "",
  "2014-2017", "Luésoni Johnson", "M.S.; Biological Sciences", "Currently a doctoral student at the University of Illinois School of information Science",
  "2013-2016", "Elizabeth Moffett", "Ph.D.; Biological Sciences", "Currently an Assistant Professor at Rocky Vista University",
  "2014-2015", "Kaleb Sellers", "M.S.; Pathology", "Currently a doctoral candidate at the University of Missoui",
  "2012-2015", "Henry Tsai", "Ph.D.; Pathobiology", "Currently an Assistant Professor at Missouri State University",
  "2009-2012", "Kandee Bain", "M.S.; Biology, CSUSB", "",
  "2008-2012", "Kim Scott", "M.S.; Biology, CSUSB", "",
  "2007-2008", "Adam Huttenlocker", "M.S.; Biology, CSUSB", "Currently an Assistant Professor at the University of Southern California",
  "2007-2008", "Candace Reno", "M.S.; Biology, CSUSB", ""
) %>% 
  detailed_entries(when = Dates, what = Name, with = Degree, where = Notes)
```


# Undergraduate Mentoring

University of Missouri only. 23 additional students at CSU San Bernardino, Brown University, and UC Riverside (2003--2012).

```{r, UG_mentoring}
tribble(
  ~ Dates, ~ Name, ~ Notes,
  "2020-Present", "Madison LaChance", "MU Cherng Summer Scholar",
  "2019-Present", "Joshua Fajardo", "",
  "2018", "Kendra Lewis", "MU School of Medicine Summer Research Intern from Washington University in St. Louis",
  "2016-2019", "Alec Wilken", "Currently doctoral student at the University of Chicago",
  "2016-2018", "Caitlyn Smith", "Currently a student in the University of Missouri School of Medicine",
  "2016-2018", "Rebecca Meyer", "Currently in medical school at the Kentucky College of Medicine",
  "2016-2017", "Nicholas Ferrari", "",
  "2016", "Jake Cooper", "NSF Inside Dinosaurs Research Fellow",
  "2016", "Eva Herbst", "NSF Inside Dinosaurs Research Fellow",
  "2014-2018", "Nicholas Bira", "C3 Hughes Research Fellow",
  "2015", "Kyle Kirkland", "MU School of Medicine Summer Research Intern from Michigan State University",
  "2014-2015", "Imran Rashid", "",
  "2014-2015", "Michael Sojka", "C3 Hughes Research Fellow, MU School of Journalism",
  "2014", "Tarrin Casey", "Currently a student in the University of Missouri School of Medicine",
  "2013", "Diana Salas", "MU School of Medicine Summer Research Intern from Indiana University"
) %>% 
  detailed_entries(when = Dates, what = Name, where = Notes)
```


```{r}
# Subset abstracts from bib_entries
Abstracts <- bib_entries %>%
    filter(str_detect(keyword, "CV/Abstracts")) %>%
    arrange(issued, author)
```


# Published Abstracts (most recent 20 of `r nrow(Abstracts)`)

```{r abstracts}
if (include_refs) {
  Abstracts %>% 
    slice_tail(n = 20)
}
```

<!--
```{r}
Other <- bib_entries %>%
    filter(str_detect(keyword, "CV/Other presentations")) %>%
    arrange(issued, author)
```

## Other Presentations (most recent 20 of `r nrow(Other)`)

```{r other}
if (include_refs) {
  Other %>% 
    slice(1:20)
}
```
-->


# Teaching Experience

## University of Missouri

```{r}
read_csv("MU_Teaching.csv", col_types = c("ccc")) %>% 
  detailed_entries(when = Dates, what = Course, where = Notes)
```


## California State University, San Bernardino

```{r, CSUSB_teaching}
tribble(
  ~ Dates, ~ Course,
  "2007-2011", "Biology of the Chordates",
  "2008-2012", "Human Physiology and Anatomy",
  "2010-2012", "Biostatistics",
  "2008, 2010, 2012", "Graduate Seminar",
  "2008-2011", "Biology Seminar",
  "2008", "Advanced Vertebrate Morphology"
) %>% 
  detailed_entries(when = Dates, what = Course)
```


# Invited Seminars

```{r, seminars}
tribble(
  ~ Dates, ~ Location,
  "2001", "University of Chicago",
  "2001", "American Museum of Natural History",
  "2007", "CSU, San Bernardino",
  "2007", "University of California, Riverside",
  "2007", "CSU, Fullerton",
  "2007", "Loma Linda University",
  "2010", "Grove High School, Redlands, CA",
  "2010", "CSU, Northridge",
  "2011", "University of Missouri",
  "2012", "La Sierra College",
  "2012", "Grinnell College",
  "2013", "MU Evolutionary Studies EvoBlitz",
  "2013", "University of Texas at Austin",
  "2013", "Saint Louis University",
  "2013", "MU Division of Biological Sciences",
  "2014", "Northeast Ohio Medical University",
  "2014", "MU Math in Life Sciences Freshman Interest Group",
  "2014", "MU LSUROP Evening Seminar Speaker",
  "2017", "MU Saturday Morning Science",
  "2018", "MU Department of Pathology and Anatomical Sciences"
) %>% 
  detailed_entries(when = Dates, what = Location)
```


# Professional Service

## Referee

- Acta Anatomica
- Acta Palaeontologica Polonica
- Acta Zoologica Sinica
- Ameghiniana
- American Journal of Physical Anthropology
- Anatomical Record
- Biology Letters
- Comparative Biochemistry and Physiology
- Current Biology
- Evolution
- IEEE Visualization & Graphics
- Integrative Organismal Biology
- International Journal of Primatology
- Journal of Anatomy
- Journal of Morphology
- Journal of Vertebrate Paleontology
- Journal of Zoology
- Nature
- Nature Communications
- Naturwissenschaften
- Palaeontology
- Paleobiology
- Paleobios
- PeerJ
- PLoS One
- Proceedings of the National Academy of Sciences USA
- Proceedings of the Royal Society (Biological Sciences)
- Quarterly Review of Biology
- Restoration Ecology
- Royal Society Open Science
- Zoological Journal of the Linnean Society
- Zoology


## NSF Panel Service

```{r, NSF_Panel}
tribble(
  ~ Dates, ~ Service,
  "2012", "Division of Evolutionary Biology -- Systematics and Biodiversity Science"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


## NSF Ad Hoc Reviewer

```{r, NSF_ad_hoc}
tribble(
  ~ Dates, ~ Service,
  "2009", "National Science Foundation -- IOB",
  "2010", "National Science Foundation -- DEB",
  "2012", "National Science Foundation -- IOB",
  "2017", "National Science Foundation -- IOB",
  "2019", "National Science Foundation -- IOB"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


## University of Missouri Research Board

```{r, research_board}
tribble(
  ~ Dates, ~ Service,
  "2015", "Ad hoc reviewer"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


## Reviewer (Textbooks)

```{r, textbooks}
tribble(
  ~ Dates, ~ Author, ~Title, ~ Publisher,
  "2003", "Miller, KR and JS Levine", "\\emph{Biology}", "Pearson-Prentice Hall",
  "2010", "Tate, P", "\\emph{Anatomy and Physiology}", "McGraw Hill",
  "2010", "Biological Sciences Curriculum Studies", "\\emph{BSCS Biology: A Human Approach}, 4th Ed.", "Kendall Hunt Publishing"
) %>% 
  detailed_entries(when = Dates, where = Author,
                   what = Title, with = Publisher, .protect=FALSE)
```


## Reviewer for Deutsche Forschungsgemeinschaft (German Research Foundation)

```{r}
tribble(
  ~ Dates, ~ Service,
  "2018", "Life Sciences 1: Molecular and Organismic Biology"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


# Department and University Service

## Current

```{r, current_service}
tribble(
  ~ Dates, ~ Service,
  "2020-Present", "MUSOM MedPrep 2 Interviewer",
  "2013-2017, 2020-Present", "PAS Director of Graduate Studies",
  "2020-Present", "School of Medicine Block 4 Planning Committee",
  "2018-Present", "MU School of Medicine Faculty Committee for Diversity and Inclusion",
  "2015-Present", "School of Medicine Advice Support and Career (ASC) Preclerkship Advisor",
  "2014-Present", "School of Medicine eResources Committee",
  "2013-2016, 2019-Present", "SOM Summer Research Internship in Medical Sciences Selection Committee",
  "2012-Present", "MU Doctoral Faculty",
  "2012-Present", "MU Graduate Faculty",
  "2012-Present", "Pathobiology Area Program Faculty"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


## Past

### University of Missouri

```{r, past_service}
tribble(
  ~ Dates, ~ Service,
  "2014-2019", "School of Medicine Block 2 Planning Committee",
  "2013, 2015-2019", "PAS Assistant Teaching Professor Search Committee",
  "2013-2015, 2018", "MUSOM Summer Research Fellow Research Mentor",
  "2013-2019", "PAS Promotion and Tenure Committee",
  "2013-2020", "PAS Director of Admissions",
  "2016-2019", "Evolution and Social Science Group (ESS) steering committee",
  "2016-2019", "MU School of Medicine Admissions Committee",
  "2016-2019", "MU Information Technology Committee",
  "2016-2018", "MU Library Committee",
  "2016", "Chair, MU Life Sciences Week Genetics, Evolution, and Environment Poster Competition",
  "2016", "MU Office of Undergraduate Research focus group",
  "2015", "Life Sciences Undergraduate Research Opportunity Program Selection Committee",
  "2014-2018", "MU Life Sciences Week poster competition judge",
  "2013-2019", "PAS Lecturer Search Committee",
  "2013-2014", "School of Medicine Block 4 Planning Committee"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


### California State University, San Bernardino

```{r, CSUSB_service}
tribble(
  ~ Dates, ~ Service,
  "2009-2012", "Institutional Animal Care and Use Committee",
  "2008-2012", "NSF Mathematics and Science Scholars Mentor",
  "2007-2012", "Pre-Dental Club Faculty Advisor",
  "2007-2012", "Health Professions Advisory Committee",
  "2007-2012", "Biology Department Webmaster",
  "2009", "College of Natural Sciences Outstanding Students Evaluation Committee"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


# Professional Organizations

- American Association of Anatomists
- International Association of Dental Research
- International Society of Vertebrate Morphology
- Society of Avian Paleontology and Evolution
- Society of Integrative and Comparative Biology
- Society of Vertebrate Paleontology


# Televised Outreach

```{r}
tribble(
  ~ Dates, ~Title, ~ Notes,
  "2009", "National Geographic Channel -- Prehistoric Predators", "National Geographic Channel's Prehistoric Predators featured an episode on phorusrhacids (also known as Terror Birds -- an extinct group of gigantic carnivorous birds from the Cenozoic of South and North America).",
  "2009", "Discovery Channel -- Megabeasts", "Discovery Channel's Megabeasts also features an episode on Terror Birds",
  "2008", "Coastline Community College", "On-camera expert on skeletal biology for an Anatomy & Physiology course produced by Coastline Community College (Orange County, CA). This course will be utilized by 2-year colleges and 4-year universities as well as broadcast locally by PBS.",
  "2008", "CBC Television Canada -- Project X", "The Project X episode 'Flight' showcases collaborative work with Drs. Sharon Swartz, Kenneth Breuer, Daniel Riskin, and Jose Iriarte-Diaz on the aeromechanics of bat flight."
) %>% 
  detailed_entries(when = Dates, what = Title, where = Notes)
```


\vfill

\vspace{3 mm}

\hrule

\vspace{3 mm}

\begin{centering}

Last updated: `r format(Sys.time(), '%d %B %Y')`

Source: \href{http://github.com/kmiddleton/cv}{\tt http://github.com/kmiddleton/cv}

Typeset with \href{https://github.com/mitchelloharawild/vitae}{vitae}

\end{centering}
