---
name: Kevin Middleton, Ph.D.
position: |
  | Associate Professor
  | Department of Pathology & Anatomical Sciences
  | University of Missouri School of Medicine
address: |
  | 1 Hospital Dr., Medical Science Building M263
  | Columbia, MO 65212
www: middletonlab.org
email: "middletonk@missouri.edu"
phone: "573 884 3192"
pubmed: kevin.middleton.1
orcid: 0000-0003-4704-1064
github: kmiddleton
scholar: Ziha7x8AAAAJ
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::hyndman:
    includes:
      in_header: "preamble.tex"
headcolor: "000090"
papersize: letterpaper
---

\renewcommand{\labelitemi}{\textbullet}

```{r setup, include=FALSE}
#remotes::install_github("kmiddleton/vitae")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)

include_refs <- FALSE
```

# Professional Experience

```{r, echo=FALSE}
tribble(
  ~ Position, ~ University, ~ Location, ~ Dates,
  "Associate Professor, Department of Pathology & Anatomical Sciences", "University of Missouri", "Columbia, MO", "2012 - Present",
  "Assistant to Associate Professor, Department of Biology", "CSU San Bernardino", "San Bernardino, CA", "2007 - 2012",
  "NIH NRSA Postdoctoral Fellow", "Brown University and University of California, Riverside", "Providence, RI and Riverside, CA", "2005 - 2007",
  "Postdoctoral Research Associate, Department of Ecology and Evolutionary Biology", "Brown University", "Providence, RI", "2003 - 2005"
) %>% 
  detailed_entries(what = Position, when = Dates,
                   where = University, with = Location)
```

# Education

```{r, echo=FALSE}
tribble(
  ~ Degree, ~ University, ~ Location, ~ Dates,
  "BS Biology, Summa Cum Laude", "Wake Forest University", "Winston-Salem, NC", "1992 - 1995",
  "PhD Ecology and Evolutionary Biology", "Brown University", "Providence, RI", "1996 - 2003"
) %>% 
  detailed_entries(when = Dates, what = University,
                   where = Degree, with = Location)
```


# Research Interests and Current Projects

My overall research focuses on form, physiology, and function of the skeletal and muscular systems in the contexts of growth, locomotion, feeding, and evolution. In my work, I integrate studies across multiple scales from micro-scale structural materials of bone to macro-scale whole bone and multi-element cranial morphology to evolutionary changes across taxa and with comparisons to extinct organisms.

## Development of Bayesian and machine learning models for the prediction of craniofacial growth in humans.

- For orthodontic and craniofacial interventions, estimation of the timing of peak growth and/or the amount of remaining growth is is important for planning treatment. We are seeking to estimate these quantities for a wide range of traits in two- and three-dimensional imaging.

## Evolution of the reptile head: integrating cranial biomechanics, muscle modeling, and brain evolution to understand cranial kinesis and diversity

- Computational modelling of cranial function has allowed us to estimate all the forces acting on the jaws and skull. We are developing techniques to apply contrast-enhanced imaging to refine muscle force estimates and generate a complete picture of head function.

## Effects of exercise and genetic background on skeletal form, physiology, and biomechanics using high activity mice as a model organism

- Although "exercise builds strong bones", genetics play a large part in bone's response to exercise. I have developed an animal model to investigate the relative roles of these two key determinants of skeletal form. 


# Awards

```{r awards, results="asis"}
tribble(
  ~ Year, ~ Award,
  2017, "School of Medicine Award for Outstanding Preclinical Faculty Education",
  2017, "Ann K. Covington Award for Undergraduate Mentoring",
  2019, "Gold Chalk Award for Graduate Teaching"
) %>%
  detailed_entries(Award, Year)
```


# Grants in Preparation

\LTXtable{\textwidth}{grants_in_prep.tex}

<!--
# Grants in Review

\LTXtable{\textwidth}{grants_in_review.tex}
-->


# Current Support

\LTXtable{\textwidth}{grants_current.tex}

# Past Grants and Fellowships

\LTXtable{\textwidth}{grants.tex}

```{r include=FALSE}
## FIXME Publications
```


# Publications

A full list of my published work can be found at: \href{https://www.ncbi.nlm.nih.gov/myncbi/kevin.middleton.1/bibliography/public/}{\color[HTML]{000090}{NIH PubMed}}


## Dissertation

```{r dissertation}
bib_entries <- bibliography_entries("Paperpile.bib")

if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Dissertation"))
}
```


## Refereed Research Papers

```{r research-papers, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Papers")) %>%
    arrange(issued, author)
}
```


## Manuscripts in Review

```{r in-review, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/In review")) %>% 
    arrange(author)
}
```


## Book Chapters

```{r book-chapters, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Book chapters")) %>%
    arrange(issued, author)
}
```


## Invited Reviews

```{r invited-reviews, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Reviews")) %>%
    arrange(issued, author)
}
```


## Book Reviews

```{r book-reviews, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Book reviews")) %>%
    arrange(issued, author)
}
```


## Published Data Sets

```{r datasets, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Datasets")) %>%
    arrange(issued, author)
}
```


## Manuscripts in Preparation

```{r in-prep, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/In prep")) %>%
    arrange(author)
}
```


# Postdoctoral Supervisor

```{r postdoc}
tribble(
  ~ Dates, ~ Name, ~ Notes,
  "2015-2018", "Alida Bailleul, PhD", "Currently an Assistant Professor at the Institute of Vertebrate Paleontology and Paleoanthropology, Beijing"
) %>% 
  detailed_entries(when = Dates, what = Name, where = Notes)
```


# Graduate Advisor

```{r, grad_advisor}
tribble(
  ~ Dates, ~ Name, ~ Degree, ~ Notes,
  "2015-2019", "Sarah Peacock", "Ph.D. University of Missouri", "Currently Assistant Teaching Professor at Northeastern University",
  "2013-2018", "Amanda Smolinsky", "Ph.D. University of Missouri", "Currently an Assistant Teaching Professor at Roanoke College",
  "2011-2012", "Katherine Johnson", "M.S., CSUSB", "Completed doctoral studies at University of California, Riverside",
  "2010-2012", "Brittney Coats", "M.S., CSUSB", "Completed doctoral studies at the University of Chicago",
  "2008-2012", "Susan Lujan", "M.S., CSUSB", "Currently a lecturer at California State University, San Bernardino"
) %>% 
  detailed_entries(when = Dates, what = Name, with = Degree, where = Notes)
```


# Graduate Committee Member

## Current

```{r, current_committee}
tribble(
  ~ Dates, ~ Name, ~ Degree,
  "2021-Present", "Wade Leibach", "M.S.; Geological Sciences",
  "2021-Present", "Delaney Ryan", "M.S.; Geological Sciences",
  "2020-Present", "Gabriel Jacobs", "Ph.D.; Geological Sciences",
  "2020-Present", "Christian Perez", "Ph.D.; Biological Sciences",
  "2019-Present", "Emily Lessner", "Ph.D.; Pathobiology",
  "2019-Present", "Samuel Sullivan", "Ph.D.; Pathobiology",
  "2019-Present", "Mikaela Pulsipher", "M.S.; Geological Sciences",
  "2018-Present", "Sean Greer", "Ph.D.; Pathobiology",
  "2016-Present", "Kaleb Sellers", "Ph.D.; Pathobiology",
  "2016-Present", "Elizabeth Cho", "Ph.D.; Anthropology",
  "2016-Present", "Deise Cruz", "Ph.D.; Biological Sciences",
  "2015-Present", "Rob'yn Johnston", "Ph.D.; Anthropology"
) %>% 
  detailed_entries(when = Dates, what = Name, with = Degree)
```


## Past

```{r, past_committee}
tribble(
  ~ Dates, ~ Name, ~ Degree, ~ Notes,
  "2017-2020", "Faye McGechie", "Ph.D.; Pathobiology", "Currently podtdoctoral researcher, University of Chicago",
  "2017-2020", "Rebecca Dirkes", "Ph.D.; Nutrition & Exercise Physiology", "Currently pursuing certificate in nutrition, University of Missouri",
  "2019-2020", "Alec Wilken", "M.S.; Pathology and Anatomical Sciences", "Currently doctoral student at University of Chicago",
  "2016-2020", "Melanie Boeyer", "Ph.D.; Pathobiology", "Currently postdoctoral research associate at the University of Missouri",
  "2015-2020", "Sharon Kuo", "Ph.D.; Pathobiology", "Currently postdoctoral research associate at Pennsylvania State University",
  "2018-2019", "Ellee Cook", "Ph.D.; Biological Sciences", "Currently a high school teacher",
  "2015-2019", "Ian Cost", "Ph.D.; Pathobiology", "Currently assistant professor at Albright College",
  "2017-2018", "Landry Konan", "M.S.; Pathology and Anatomical Sciences", "",
  "2017-2018", "Stephanie Rosbach", "M.S.; Geological Sciences", "",
  "2016-2018", "Tara Selly", "Ph.D.; Geological Sciences", "Currently research associate at the University of Missouri",
  "2015-2017", "Edward Ramirez", "M.S.; Biological Sciences", "",
  "2015-2017", "Steven Hanson", "Ph.D.; Pathobiology", "",
  "2014-2017", "Luésoni Johnson", "M.S.; Biological Sciences", "Currently a doctoral student at the University of Illinois School of information Science",
  "2013-2016", "Elizabeth Moffett", "Ph.D.; Biological Sciences", "Currently an Assistant Professor at Rocky Vista University",
  "2014-2015", "Kaleb Sellers", "M.S.; Pathology", "",
  "2012-2015", "Henry Tsai", "Ph.D.; Pathobiology", "Currently an Assistant Professor at Missouri State University",
  "2009-2012", "Kandee Bain", "M.S.; Biology, CSUSB", "",
  "2008-2012", "Kim Scott", "M.S.; Biology, CSUSB", "",
  "2007-2008", "Adam Huttenlocker", "M.S.; Biology, CSUSB", "Currently an Assistant Professor at the University of Southern California",
  "2007-2008", "Candace Reno", "M.S.; Biology, CSUSB", ""
) %>% 
  detailed_entries(when = Dates, what = Name, with = Degree, where = Notes)
```


# Undergraduate Mentoring

University of Missouri only. 23 additional students at CSU San Bernardino, Brown University, and UC Riverside (2003--2012).

```{r, UG_mentoring}
tribble(
  ~ Dates, ~ Name, ~ Notes,
  "2020-Present", "Madison LaChance", "MU Cherng Summer Scholar",
  "2019-Present", "Joshua Fajardo", "",
  "2018", "Kendra Lewis", "MU School of Medicine Summer Research Intern from Washington University in St. Louis",
  "2016-2019", "Alec Wilken", "Currently doctoral student at the University of Chicago",
  "2016-2018", "Caitlyn Smith", "Currently a student in the University of Missouri School of Medicine",
  "2016-2018", "Rebecca Meyer", "Currently in medical school at the Kentucky College of Medicine",
  "2016-2017", "Nicholas Ferrari", "",
  "2016", "Jake Cooper", "NSF Inside Dinosaurs Research Fellow",
  "2016", "Eva Herbst", "NSF Inside Dinosaurs Research Fellow",
  "2014-2018", "Nicholas Bira", "C3 Hughes Research Fellow",
  "2015", "Kyle Kirkland", "MU School of Medicine Summer Research Intern from Michigan State University",
  "2014-2015", "Imran Rashid", "",
  "2014-2015", "Michael Sojka", "C3 Hughes Research Fellow, MU School of Journalism",
  "2014", "Tarrin Casey", "Currently a student in the University of Missouri School of Medicine",
  "2013", "Diana Salas", "MU School of Medicine Summer Research Intern from Indiana University"
) %>% 
  detailed_entries(when = Dates, what = Name, where = Notes)
```


```{r}
# Subset abstracts from bib_entries
Abstracts <- bib_entries %>%
    filter(str_detect(keyword, "CV/Abstracts")) %>%
    arrange(issued, author)
```


# Published Abstracts (most recent 20 of `r nrow(Abstracts)`)

```{r abstracts}
if (include_refs) {
  Abstracts %>% 
    slice_tail(n = 20)
}
```

<!--
```{r}
Other <- bib_entries %>%
    filter(str_detect(keyword, "CV/Other presentations")) %>%
    arrange(issued, author)
```

## Other Presentations (most recent 20 of `r nrow(Other)`)

```{r other}
if (include_refs) {
  Other %>% 
    slice(1:20)
}
```
-->


# Teaching Experience

## University of Missouri

```{r}
read_csv("MU_Teaching.csv", col_types = c("ccc")) %>% 
  detailed_entries(when = Dates, what = Course, where = Notes)
```


## California State University, San Bernardino

```{r, CSUSB_teaching}
tribble(
  ~ Dates, ~ Course,
  "2007-2011", "Biology of the Chordates",
  "2008-2012", "Human Physiology and Anatomy",
  "2010-2012", "Biostatistics",
  "2008, 2010, 2012", "Graduate Seminar",
  "2008-2011", "Biology Seminar",
  "2008", "Advanced Vertebrate Morphology"
) %>% 
  detailed_entries(when = Dates, what = Course)
```


# Invited Seminars

```{r, seminars}
tribble(
  ~ Dates, ~ Location,
  "2001", "University of Chicago",
  "2001", "American Museum of Natural History",
  "2007", "CSU, San Bernardino",
  "2007", "University of California, Riverside",
  "2007", "CSU, Fullerton",
  "2007", "Loma Linda University",
  "2010", "Grove High School, Redlands, CA",
  "2010", "CSU, Northridge",
  "2011", "University of Missouri",
  "2012", "La Sierra College",
  "2012", "Grinnell College",
  "2013", "MU Evolutionary Studies EvoBlitz",
  "2013", "University of Texas at Austin",
  "2013", "Saint Louis University",
  "2013", "MU Division of Biological Sciences",
  "2014", "Northeast Ohio Medical University",
  "2014", "MU Math in Life Sciences Freshman Interest Group",
  "2014", "MU LSUROP Evening Seminar Speaker",
  "2017", "MU Saturday Morning Science",
  "2018", "MU Department of Pathology and Anatomical Sciences"
) %>% 
  detailed_entries(when = Dates, what = Location)
```


# Professional Service

## Referee

- Acta Anatomica
- Acta Palaeontologica Polonica
- Acta Zoologica Sinica
- Ameghiniana
- American Journal of Physical Anthropology
- Anatomical Record
- Biology Letters
- Comparative Biochemistry and Physiology
- Current Biology
- Evolution
- IEEE Visualization & Graphics
- Integrative Organismal Biology
- International Journal of Primatology
- Journal of Anatomy
- Journal of Morphology
- Journal of Vertebrate Paleontology
- Journal of Zoology
- Nature
- Nature Communications
- Naturwissenschaften
- Palaeontology
- Paleobiology
- Paleobios
- PeerJ
- PLoS One
- Proceedings of the National Academy of Sciences USA
- Proceedings of the Royal Society (Biological Sciences)
- Quarterly Review of Biology
- Restoration Ecology
- Royal Society Open Science
- Zoological Journal of the Linnean Society
- Zoology


## NSF Panel Service

```{r, NSF_Panel}
tribble(
  ~ Dates, ~ Service,
  "2012", "Division of Evolutionary Biology -- Systematics and Biodiversity Science"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


## NSF Ad Hoc Reviewer

```{r, NSF_ad_hoc}
tribble(
  ~ Dates, ~ Service,
  "2009", "National Science Foundation -- IOB",
  "2010", "National Science Foundation -- DEB",
  "2012", "National Science Foundation -- IOB",
  "2017", "National Science Foundation -- IOB",
  "2019", "National Science Foundation -- IOB"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


## University of Missouri Research Board

```{r, research_board}
tribble(
  ~ Dates, ~ Service,
  "2015", "Ad hoc reviewer"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


## Reviewer (Textbooks)

```{r, textbooks}
tribble(
  ~ Dates, ~ Author, ~Title, ~ Publisher,
  "2003", "Miller, KR and JS Levine", "Biology", "Pearson-Prentice Hall",
  "2010", "Tate, P", "Anatomy and Physiology", "McGraw Hill",
  "2010", "Biological Sciences Curriculum Studies", "BSCS Biology: A Human Approach. 4th Ed.", "Kendall Hunt Publishing"
) %>% 
  detailed_entries(when = Dates, where = Author, what = Title, with = Publisher)
```


## Reviewer for Deutsche Forschungsgemeinschaft (German Research Foundation)

```{r}
tribble(
  ~ Dates, ~ Service,
  "2018", "Life Sciences 1: Molecular and Organismic Biology"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


# Department and University Service

## Current

```{r, current_service}
tribble(
  ~ Dates, ~ Service,
  "2020-Present", "MUSOM MedPrep 2 Interviewer",
  "2013-2017, 2020-Present", "PAS Director of Graduate Studies",
  "2020-Present", "School of Medicine Block 4 Planning Committee",
  "2018-Present", "MU School of Medicine Faculty Committee for Diversity and Inclusion",
  "2015-Present", "School of Medicine Advice Support and Career (ASC) Preclerkship Advisor",
  "2014-Present", "School of Medicine eResources Committee",
  "2013-2016, 2019-Present", "SOM Summer Research Internship in Medical Sciences Selection Committee",
  "2012-Present", "MU Doctoral Faculty",
  "2012-Present", "MU Graduate Faculty",
  "2012-Present", "Pathobiology Area Program Faculty"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


## Past

### University of Missouri

```{r, past_service}
tribble(
  ~ Dates, ~ Service,
  "2014-2019", "School of Medicine Block 2 Planning Committee",
  "2013, 2015-2019", "PAS Assistant Teaching Professor Search Committee",
  "2013-2019", "PAS Promotion and Tenure Committee",
  "2013-2020", "PAS Director of Admissions",
  "2016-2019", "Evolution and Social Science Group (ESS) steering committee",
  "2016-2019", "MU School of Medicine Admissions Committee",
  "2016-2019", "MU Information Technology Committee",
  "2016-2018", "MU Library Committee",
  "2016", "Chair, MU Life Sciences Week Genetics, Evolution, and Environment Poster Competition",
  "2016", "MU Office of Undergraduate Research focus group",
  "2015", "Life Sciences Undergraduate Research Opportunity Program Selection Committee",
  "2014-2018", "MU Life Sciences Week poster competition judge",
  "2013-2019", "PAS Lecturer Search Committee",
  "2013-2014", "School of Medicine Block 4 Planning Committee"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


### California State University, San Bernardino

```{r, CSUSB_service}
tribble(
  ~ Dates, ~ Service,
  "2009-2012", "Institutional Animal Care and Use Committee",
  "2008-2012", "NSF Mathematics and Science Scholars Mentor",
  "2007-2012", "Pre-Dental Club Faculty Advisor",
  "2007-2012", "Health Professions Advisory Committee",
  "2007-2012", "Biology Department Webmaster",
  "2009", "College of Natural Sciences Outstanding Students Evaluation Committee"
) %>% 
  detailed_entries(when = Dates, what = Service)
```


# Professional Organizations

- American Association of Anatomists
- International Association of Dental Research
- International Society of Vertebrate Morphology
- Society of Avian Paleontology and Evolution
- Society of Integrative and Comparative Biology
- Society of Vertebrate Paleontology


# Televised Outreach

```{r}
tribble(
  ~ Dates, ~Title, ~ Notes,
  "2009", "National Geographic Channel -- Prehistoric Predators", "National Geographic Channel's Prehistoric Predators featured an episode on phorusrhacids (also known as Terror Birds -- an extinct group of gigantic carnivorous birds from the Cenozoic of South and North America).",
  "2009", "Discovery Channel -- Megabeasts", "Discovery Channel's Megabeasts also features an episode on Terror Birds",
  "2008", "Coastline Community College", "On-camera expert on skeletal biology for an Anatomy & Physiology course produced by Coastline Community College (Orange County, CA). This course will be utilized by 2-year colleges and 4-year universities as well as broadcast by PBS.",
  "2008", "CBC Television Canada -- Project X", "The Project X episode 'Flight' showcases collaborative work with Drs. Sharon Swartz, Kenneth Breuer, Daniel Riskin, and Jose Iriarte-Diaz on the aeromechanics of bat flight."
) %>% 
  detailed_entries(when = Dates, what = Title, where = Notes)
```


\vfill

\vspace{3 mm}

\hrule

\vspace{3 mm}

\begin{centering}

Last updated: `r format(Sys.time(), '%d %B %Y')`

Source: \href{http://github.com/kmiddleton/cv}{\tt http://github.com/kmiddleton/cv}

Typeset with \href{https://github.com/mitchelloharawild/vitae}{vitae}

\end{centering}
