---
name: Kevin Middleton, Ph.D.
position: |
  | Associate Professor
  | Division of Biological Sciences
  | University of Missouri
address: |
  | 224 Tucker Hall
  | Columbia, MO 65211
www: middletonlab.org
email: "middletonk@missouri.edu"
pubmed: kevin.middleton.1
orcid: 0000-0003-4704-1064
github: kmiddleton
scholar: Ziha7x8AAAAJ
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
headcolor: 10069B
papersize: letterpaper
bib: "cell-numeric.csl"
---

\renewcommand{\labelitemi}{\textbullet}

```{r setup, include=FALSE}
#remotes::install_github("kmiddleton/vitae")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(readxl)

include_refs <- TRUE
```

```{r include=FALSE}
## FIXME Publications


```


# Professional Experience

```{r, echo=FALSE}
read_csv("Professional_Experience.csv", show_col_types = FALSE) |> 
  detailed_entries(what = Position,
                   when = Dates,
                   where = University,
                   with = Location)
```


# Education

```{r, echo=FALSE}
read_csv("Education.csv", show_col_types = FALSE) |> 
  detailed_entries(when = Dates,
                   what = University,
                   where = Degree,
                   with = Location)
```


# Research Interests and Current Projects

My overall research focuses on form, physiology, and function of the skeletal and muscular systems in the contexts of growth, locomotion, feeding, and evolution. In my work, I integrate studies across multiple scales from micro-scale structural materials of bone to macro-scale whole bone and multi-element cranial morphology to evolutionary changes across taxa and with comparisons to extinct organisms.

## Development of Bayesian and machine learning models for the prediction of craniofacial growth in humans.

- For orthodontic and craniofacial interventions, estimation of the timing of peak growth and/or the amount of remaining growth is important for planning treatment. We are seeking to estimate these quantities for a wide range of traits in two- and three-dimensional imaging.

## Evolution of the reptile head: integrating cranial biomechanics, muscle modeling, and brain evolution to understand cranial kinesis and diversity

- Computational modelling of cranial function has allowed us to estimate all the forces acting on the jaws and skull. We are developing techniques to apply contrast-enhanced imaging to refine muscle force estimates and generate a complete picture of head function.

## Effects of exercise and genetic background on skeletal form, physiology, and biomechanics using high activity mice as a model organism

- Although "exercise builds strong bones", genetics play a large part in bone's response to exercise. I have developed an animal model to investigate the relative roles of these two key determinants of skeletal form. 


# Awards

```{r awards, results="asis"}
tribble(
  ~ Year, ~ Award,
  2019, "Gold Chalk Award for Graduate Teaching",
  2017, "School of Medicine Award for Outstanding Preclinical Faculty Education",
  2017, "Ann K. Covington Award for Undergraduate Mentoring"
) |>
  detailed_entries(when = Year,
                   what = Award)
```


# Current Support

```{r}
read_csv("Current_Support.csv", show_col_types = FALSE) |> 
  detailed_entries(when = Dates,
                   what = Title,
                   with = Agency,
                   where = PIs,
                   why = Notes,
                   .protect = FALSE)
```


# Grants in Review

```{r}
read_csv("Grants_in_Review.csv", show_col_types = FALSE) |> 
  detailed_entries(when = Dates,
                   what = Title,
                   with = Agency,
                   where = PIs,
                   .protect = FALSE)
```



```{r, eval=FALSE}
# Grants in Preparation
read_csv("Grants_in_Preparation.csv", show_col_types = FALSE) |> 
  detailed_entries(when = Dates,
                   what = Title,
                   with = Agency,
                   where = PIs,
                   .protect = FALSE)
```


# Past Grants and Fellowships

```{r}
read_csv("Past_Grants.csv", show_col_types = FALSE) |> 
  detailed_entries(when = Dates,
                   what = Title,
                   with = Agency,
                   where = PIs,
                   why = Notes,
                   .protect = FALSE)
```

# Publications

A full list of my published work can be found at: \href{https://www.ncbi.nlm.nih.gov/myncbi/kevin.middleton.1/bibliography/public/}{\color[HTML]{000090}{NIH PubMed}}


## Dissertation

```{r}
# Load bib file
bib_entries <- bibliography_entries("Paperpile.bib")
```

```{r doctoral-dissertation, eval=TRUE}
if (include_refs) {
  bibliography_entries("Dissertation.bib")
}
```


## Refereed Research Papers

```{r research-papers, eval=TRUE}
if (include_refs) {
  bibliography_entries("Papers.bib") |> arrange(issued)
}
```


## Manuscripts in Review

```{r in-review, eval=TRUE}
if (include_refs) {
  bibliography_entries("In_review.bib")
}
```


## Preprints

```{r preprints, eval=TRUE}
if (include_refs) {
  bibliography_entries("Preprints.bib")
}
```


## Book Chapters

```{r book-chapters, eval=TRUE}
if (include_refs) {
  bibliography_entries("Book_chapters.bib")
}
```


## Invited Reviews

```{r invited-reviews, eval=TRUE}
if (include_refs) {
  bibliography_entries("Reviews.bib")
}
```


## Book Reviews

```{r book-reviews, eval=TRUE}
if (include_refs) {
  bibliography_entries("Book_reviews.bib")
}
```


## Published Data Sets

```{r datasets, eval=TRUE}
if (include_refs) {
  bibliography_entries("Datasets.bib") |> arrange(issued)
}
```


## Manuscripts in Preparation

```{r in-prep, eval=TRUE}
if (include_refs) {
  bibliography_entries("In_prep.bib")
}
```


# Postdoctoral Supervisor

```{r postdoc}
tribble(
  ~ Dates, ~ Name, ~ Notes,
  "2015-2018", "Alida Bailleul, PhD", "Currently an Assistant Professor, Institute of Vertebrate Paleontology and Paleoanthropology, Beijing"
) |> 
  detailed_entries(when = Dates,
                   what = Name,
                   where = Notes)
```


# Graduate Advisor

```{r, grad_advisor}
tribble(
  ~ Dates, ~ Name, ~ Degree, ~ Notes,
  "2015-2019", "Sarah Peacock", "Ph.D. University of Missouri", "Currently Assistant Teaching Professor at Northeastern University",
  "2013-2018", "Amanda Smolinsky", "Ph.D. University of Missouri", "Currently Assistant Professor at St. Norbert College",
  "2011-2012", "Katherine Johnson", "M.S., CSUSB", "Completed doctoral studies at University of California, Riverside",
  "2010-2012", "Brittney Coats", "M.S., CSUSB", "Completed doctoral studies at the University of Chicago",
  "2008-2012", "Susan Lujan", "M.S., CSUSB", ""
) |> 
  detailed_entries(when = Dates,
                   what = Name,
                   with = Degree,
                   where = Notes)
```


# Graduate Committee Member

## Current

```{r, current_committee}
tribble(
  ~ Dates, ~ Name, ~ Degree,
  "2025-Present", "Diane Cordero", "Ph.D.; Biological Sciences",
  "2024-Present", "Elyssa McCulloch", "Ph.D.; School of Natural Resources",
  "2024-Present", "Tom Burges", "Ph.D.; Biological Sciences",
  "2024-Present", "Nadine Steer", "Ph.D.; Pathobiology",
  "2024-Present", "Peyton Warren", "Ph.D.; Biological Sciences",
  "2023-Present", "Olivia Bongiovi", "Ph.D.; Natural Resources",
  "2023-Present", "Amy Lagorio", "Ph.D.; Pathobiology",
  "2023-Present", "Christopher Zobek", "Ph.D.; Pathobiology",
  "2023-Present", "Esdras Tuyishimire", "Ph.D.; Biologcal Sciences",
  "2021-Present", "John Fortner", "Ph.D.; Pathobiology"
) |> 
  detailed_entries(when = Dates,
                   what = Name,
                   with = Degree)
```


## Past

```{r, past_committee}
tribble(
  ~ Dates, ~ Name, ~ Degree, ~ Notes,
  "2024-2025", "Audrey Williams", "M.S.; Geology; Missouri S&T", "",
  "2024-2025", "Emma Cooney", "M.S.; Pathology and Anatomical Sciences", "",
  "2020-2025", "Christian Perez", "Ph.D.; Biological Sciences", "",
  "2021-2024", "Mara Fields", "M.S.; Pathology and Anatomical Sciences", "Currently employed in industry",
  "2015-2023", "Rob'yn Johnston", "Ph.D.; Anthropology", "Currently employed in industry",
  "2018-2023", "Austin Lawrence", "Ph.D.; Pathobiology", "Postdoctoral researcher, University of Chicago",
  "2020-2022", "Gabriel Jacobs", "Ph.D.; Geological Sciences", "Lecturer, Cornell College",
  "2018-2022", "Sean Greer", "Ph.D.; Pathobiology", "Lecturer, University of Missouri",
  "2018-2022", "Emily Lessner", "Ph.D.; Pathobiology", "Petrified National Forest",
  "2016-2022", "Elizabeth Cho", "Ph.D.; Anthropology", "Assistant professor, UNTHSC",
  "2016-2021", "Deise Cruz", "Ph.D.; Biological Sciences", " ",
  "2016-2021", "Kaleb Sellers", "Ph.D.; Pathobiology", "Postdoctoral researcher, University of Chicago",
  "2017-2021", "Faye McGechie", "Ph.D.; Pathobiology", "Assistant professor, University of Arizona",
  "2017-2020", "Rebecca Dirkes", "Ph.D.; Nutrition & Exercise Physiology", " ",
  "2019-2020", "Mikaela Pulsipher", "M.S.; Geological Sciences", " ",
  "2019-2020", "Alec Wilken", "M.S.; Pathology and Anatomical Sciences", "Doctoral student, University of Chicago",
  "2016-2020", "Melanie Boeyer", "Ph.D.; Pathobiology", "Research assistant professor, University of Missouri",
  "2015-2020", "Sharon Kuo", "Ph.D.; Pathobiology", "Assistant professor, University of Minnesota Duluth",
  "2018-2019", "Ellee Cook", "Ph.D.; Biological Sciences", "Teaching high school science",
  "2015-2019", "Ian Cost", "Ph.D.; Pathobiology", "Assistant professor, Albright College",
  "2017-2018", "Landry Konan", "M.S.; Pathology and Anatomical Sciences", "Fulbright Fellow",
  "2017-2018", "Stephanie Rosbach", "M.S.; Geological Sciences", "",
  "2016-2018", "Tara Selly", "Ph.D.; Geological Sciences", "Research assistant professor, University of Missouri",
  "2015-2017", "Edward Ramirez", "M.S.; Biological Sciences", "",
  "2015-2017", "Steven Hanson", "Ph.D.; Pathobiology", "",
  "2014-2017", "Luésoni Johnson", "M.S.; Biological Sciences", "Doctoral student, University of Illinois School of information Science",
  "2013-2016", "Elizabeth Moffett", "Ph.D.; Biological Sciences", "Assistant professor, Rocky Vista University",
  "2014-2015", "Kaleb Sellers", "M.S.; Pathology", "PhD, University of Missoui",
  "2012-2015", "Henry Tsai", "Ph.D.; Pathobiology", "Assistant Professor, Southern Connecticut State University",
  "2009-2012", "Kandee Bain", "M.S.; Biology, CSUSB", "",
  "2008-2012", "Kim Scott", "M.S.; Biology, CSUSB", "",
  "2007-2008", "Adam Huttenlocker", "M.S.; Biology, CSUSB", "Assistant Professor, University of Southern California",
  "2007-2008", "Candace Reno", "M.S.; Biology, CSUSB", ""
) |> 
  detailed_entries(when = Dates,
                   what = Name,
                   with = Degree,
                   where = Notes)
```


# Undergraduate Mentoring

33 additional students at University of Missouri, CSU San Bernardino, Brown University, and UC Riverside.

```{r, UG_mentoring}
tribble(
  ~ Dates, ~ Name, ~ Notes,
  "2024-Present", "Gabriella Ramirez", "MU Discovery Fellow; NIH MARC Fellow; Fulbright MITACS Fellow",
  "2021-2023", "Adam Albright", "MU A&S Summer Scholar; UMKC School of Dentistry",
  "2021-2022", "Kayla Robinson", "MU DBS Honors Student",
  "2020-2022", "Madison LaChance", "MU Cherng Summer Scholar",
  "2019-2022", "Joshua Fajardo", "",
  "2018-2021", "Caleb Lee", "KCU School of Medicine",
  "2018", "Kendra Lewis", "MU School of Medicine Summer Research Intern from Washington University in St. Louis",
  "2016-2019", "Alec Wilken", "University of Chicago",
  "2016-2018", "Caitlyn Smith", "University of Missouri School of Medicine",
  "2016-2018", "Rebecca Meyer", "Kentucky College of Medicine",
  "2016-2017", "Nicholas Ferrari", "",
  "2016", "Jake Cooper", "NSF Inside Dinosaurs Research Fellow",
  "2016", "Eva Herbst", "NSF Inside Dinosaurs Research Fellow; Royal Veterinary College and ETH Zurich",
  "2014-2018", "Nicholas Bira", "C3 Hughes Research Fellow; PhD Oregon State University",
  "2015", "Kyle Kirkland", "MU School of Medicine Summer Research Intern from Michigan State University",
  "2014-2015", "Imran Rashid", "",
  "2014-2015", "Michael Sojka", "C3 Hughes Research Fellow, MU School of Journalism",
  "2014", "Tarrin Casey, MD", "University of Missouri School of Medicine",
  "2013", "Diana Salas", "MU School of Medicine Summer Research Intern from Indiana University"
) |> 
  detailed_entries(when = Dates,
                   what = Name,
                   where = Notes)
```


```{r}
# Subset abstracts from bib_entries
# Add
#
Abstracts <-   bibliography_entries("Abstracts.bib")
```


# Published Abstracts (most recent 30 of `r nrow(Abstracts)`)

```{r abstracts}
if (include_refs) {
  Abstracts |> 
    slice_head(n = 30)
}
```

<!--
```{r}
Other <- bib_entries |>
filter(str_detect(keyword, "CV/Other presentations")) |>
arrange(issued, author)
```

## Other Presentations (most recent 20 of `r nrow(Other)`)

```{r other}
if (include_refs) {
Other |> 
slice(1:20)
}
```
-->


# Teaching Experience

## University of Missouri

```{r}
read_csv("MU_Teaching.csv", col_types = c("ccc")) |> 
  detailed_entries(when = Dates, what = Course, where = Notes)
```


## California State University, San Bernardino

```{r, CSUSB_teaching}
tribble(
  ~ Dates, ~ Course,
  "2007-2011", "Biology of the Chordates",
  "2008-2012", "Human Physiology and Anatomy",
  "2010-2012", "Biostatistics",
  "2008, 2010, 2012", "Graduate Seminar",
  "2008-2011", "Biology Seminar",
  "2008", "Advanced Vertebrate Morphology"
) |> 
  detailed_entries(when = Dates,
                   what = Course)
```


# Invited Seminars

```{r, seminars}
tribble(
  ~ Dates, ~ Location,
  "2023", "New Mexico State University",
  "2022", "MU Undergraduate Summer Research Program",
  "2021", "MU Division of Biological Sciences",
  "2018", "MU Department of Pathology and Anatomical Sciences",
  "2017", "MU Saturday Morning Science",
  "2014", "MU LSUROP Evening Seminar Speaker",
  "2014", "MU Math in Life Sciences Freshman Interest Group",
  "2014", "Northeast Ohio Medical University",
  "2013", "MU Division of Biological Sciences",
  "2013", "Saint Louis University",
  "2013", "University of Texas at Austin",
  "2013", "MU Evolutionary Studies EvoBlitz",
  "2012", "Grinnell College",
  "2012", "La Sierra College",
  "2011", "University of Missouri",
  "2010", "CSU, Northridge",
  "2010", "Grove High School, Redlands, CA",
  "2007", "Loma Linda University",
  "2007", "CSU, Fullerton",
  "2007", "University of California, Riverside",
  "2007", "CSU, San Bernardino",
  "2001", "American Museum of Natural History",
  "2001", "University of Chicago"
) |> 
  detailed_entries(when = Dates,
                   what = Location)
```


# Professional Service

## Referee

- Acta Anatomica
- Acta Palaeontologica Polonica
- Acta Zoologica Sinica
- Ameghiniana
- American Journal of Physical Anthropology
- Anatomical Record
- Biology Letters
- Comparative Biochemistry and Physiology
- Current Biology
- Evolution
- IEEE Visualization & Graphics
- Integrative Organismal Biology
- International Journal of Primatology
- Journal of Anatomy
- Journal of Morphology
- Journal of Vertebrate Paleontology
- Journal of Zoology
- Nature
- Nature Communications
- Naturwissenschaften
- Palaeontology
- Paleobiology
- Paleobios
- PeerJ
- PLoS One
- Proceedings of the National Academy of Sciences USA
- Proceedings of the Royal Society (Biological Sciences)
- Quarterly Review of Biology
- Restoration Ecology
- Royal Society Open Science
- Zoological Journal of the Linnean Society
- Zoology


## NSF Panel Service

```{r, NSF_Panel}
tribble(
  ~ Dates, ~ Service,
  "2012", "Division of Evolutionary Biology -- Systematics and Biodiversity Science"
) |> 
  detailed_entries(when = Dates,
                   what = Service)
```


## NSF Ad Hoc Reviewer

```{r, NSF_ad_hoc}
tribble(
  ~ Dates, ~ Service,
  "2009", "National Science Foundation -- IOB",
  "2010", "National Science Foundation -- DEB",
  "2012", "National Science Foundation -- IOB",
  "2017", "National Science Foundation -- IOB",
  "2019", "National Science Foundation -- IOB"
) |> 
  detailed_entries(when = Dates,
                   what = Service)
```


## University of Missouri Research Board

```{r, research_board}
tribble(
  ~ Dates, ~ Service,
  "2015", "Ad hoc reviewer"
) |> 
  detailed_entries(when = Dates,
                   what = Service)
```


## Reviewer (Textbooks)

```{r, textbooks}
tribble(
  ~ Dates, ~ Author, ~Title, ~ Publisher,
  "2003", "Miller, KR and JS Levine", "\\emph{Biology}", "Pearson-Prentice Hall",
  "2010", "Tate, P", "\\emph{Anatomy and Physiology}", "McGraw Hill",
  "2010", "Biological Sciences Curriculum Studies", "\\emph{BSCS Biology: A Human Approach}, 4th Ed.", "Kendall Hunt Publishing"
) |> 
  detailed_entries(when = Dates,
                   where = Author,
                   what = Title,
                   with = Publisher,
                   .protect = FALSE)
```


## Reviewer for Deutsche Forschungsgemeinschaft (German Research Foundation)

```{r}
tribble(
  ~ Dates, ~ Service,
  "2018", "Life Sciences 1: Molecular and Organismic Biology"
) |> 
  detailed_entries(when = Dates,
                   what = Service)
```


# Department and University Service

## Current

```{r, current_service}
tribble(
  ~ Dates, ~ Service,
  "2024-Present", "Show Me Research Week Judge",
  "2024-Present", "Division of Biological Sciences Divisional Council",
  "2023-Present", "MedOpp Interviewer",
  "2022-Present", "Division of Biological Sciences Graduate Education Committee",
  "2022-Present", "Division of Biological Sciences Graduate Faculty",
  "2020-Present", "MUSOM MedPrep 2 Application Review",
  "2020-Present", "MUSOM MedPrep 2 Interview Committee",
  "2022-Present", "MUSOM PAWS Program Committee",
  "2013-2016, 2019-Present", "SOM Summer Research Internship in Medical Sciences Selection Committee",
  "2012-Present", "MU Doctoral Faculty",
  "2012-Present", "MU Graduate Faculty",
  "2012-Present", "Pathobiology Area Doctoral Program Graduate Faculty"
) |> 
  detailed_entries(when = Dates,
                   what = Service)
```


## Past

### University of Missouri

```{r, past_service}
tribble(
  ~ Dates, ~ Service,
  "2013-2017, 2020-2022", "PAS Director of Graduate Studies",
  "2020-2022", "SOM Block 4 Planning Committee",
  "2018-2022", "SOM Faculty Committee for Diversity and Inclusion",
  "2015-2022", "SOM Advice Support and Career (ASC) Preclerkship Advisor",
  "2014-2019", "SOM eResources Committee",
  "2014-2019", "SOM Block 2 Planning Committee",
  "2013, 2015-2019", "PAS Assistant Teaching Professor Search Committee",
  "2013-2015, 2018", "SOM Summer Research Fellow Research Mentor",
  "2013-2019", "PAS Promotion and Tenure Committee",
  "2013-2020", "PAS Director of Admissions",
  "2016-2019", "Evolution and Social Science Group (ESS) steering committee",
  "2016-2019", "MU School of Medicine Admissions Committee",
  "2016-2019", "MU Information Technology Committee",
  "2016-2018", "MU Library Committee",
  "2016", "Chair, MU Life Sciences Week Genetics, Evolution, and Environment Poster Competition",
  "2016", "MU Office of Undergraduate Research focus group",
  "2015", "Life Sciences Undergraduate Research Opportunity Program Selection Committee",
  "2014-2018", "MU Life Sciences Week poster competition judge",
  "2013-2019", "PAS Lecturer Search Committee",
  "2013-2014", "SOM Block 4 Planning Committee"
) |> 
  detailed_entries(when = Dates,
                   what = Service)
```


### California State University, San Bernardino

```{r, CSUSB_service}
tribble(
  ~ Dates, ~ Service,
  "2009-2012", "Institutional Animal Care and Use Committee",
  "2008-2012", "NSF Mathematics and Science Scholars Mentor",
  "2007-2012", "Pre-Dental Club Faculty Advisor",
  "2007-2012", "Health Professions Advisory Committee",
  "2007-2012", "Biology Department Webmaster",
  "2009", "College of Natural Sciences Outstanding Students Evaluation Committee"
) |> 
  detailed_entries(when = Dates,
                   what = Service)
```


# Professional Organizations

- American Association of Anatomists
- International Association of Dental Research
- International Society of Vertebrate Morphology
- Society of Integrative and Comparative Biology


# Televised Outreach

```{r}
tribble(
  ~ Dates, ~Title, ~ Notes,
  "2009", "National Geographic Channel -- Prehistoric Predators", "National Geographic Channel's Prehistoric Predators featured an episode on phorusrhacids (also known as Terror Birds -- an extinct group of gigantic carnivorous birds from the Cenozoic of South and North America).",
  "2009", "Discovery Channel -- Megabeasts", "Discovery Channel's Megabeasts also features an episode on Terror Birds",
  "2008", "Coastline Community College", "On-camera expert on skeletal biology for an Anatomy & Physiology course produced by Coastline Community College (Orange County, CA). This course will be utilized by 2-year colleges and 4-year universities as well as broadcast locally by PBS.",
  "2008", "CBC Television Canada -- Project X", "The Project X episode 'Flight' showcases collaborative work with Drs. Sharon Swartz, Kenneth Breuer, Daniel Riskin, and Jose Iriarte-Diaz on the aeromechanics of bat flight."
) |> 
  detailed_entries(when = Dates,
                   what = Title,
                   where = Notes)
```


\vfill

\vspace{3 mm}

\hrule

\vspace{3 mm}

\begin{centering}

Last updated: `r format(Sys.time(), '%d %B %Y')`

Source: \href{http://github.com/kmiddleton/cv}{\tt http://github.com/kmiddleton/cv}

Typeset with \href{https://github.com/mitchelloharawild/vitae}{vitae}

\end{centering}
