---
name: "Kevin Middleton, Ph.D."
position: "Associate Professor"
address: "Department of Pathology & Anatomical Sciences"
address2: "University of Missouri School of Medicine"
address3: "Medical Science Building M263, 1 Hospital Dr."
address4: "Columbia, MO 65212"
www: middletonlab.org
email: "middletonk@missouri.edu"
phone: "573 884 3192"
pubmed: kevin.middleton.1
orcid: 0000-0003-4704-1064
github: kmiddleton
scholar: Ziha7x8AAAAJ
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::middleton:
    latex_engine: pdflatex
    keep_tex: no
    includes:
      in_header: "preamble.tex"
---

```{r setup, include=FALSE}
#remotes::install_github("kmiddleton/vitae")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
options(tinytex.verbose = TRUE)

include_refs <- TRUE
```

# Professional Experience

```{r, echo=FALSE}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "Associate Professor", "University of Missouri", "Department of Pathology & Anatomical Sciences", "2012 - Pres.",
  "Associate Professor", "CSU San Bernardino", "Department of Biology", "2011 - 2012",
  "Assistant Professor", "CSU San Bernardino", "Department of Biology", "2007 - 2011",
  "NIH NRSA Postdoctoral Fellow", "Brown University and University of California, Riverside", "Effects of Genetics, Exercise, and Age on Bone Mechanics", "2005 - 2007",
  "Postdoctoral Research Associate", "Brown University", "Department of Ecology and Evolutionary Biology", "2003 - 2005"
) %>% 
  detailed_entries(degree, dates, uni, loc)
```

# Education

```{r, echo=FALSE}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "BS Biology", "Wake Forest University", "Summa Cum Laude", "1992 - 1995",
  "PhD Ecology and Evolutionary Biology", "Brown University", "Morphology, evolution, and function of the avian hallux", "1996 - 2003"
) %>% 
  detailed_entries(degree, dates, uni, loc)
```

# Research Interests

My research focuses on musculoskeletal physiology, form, and function in the contexts of animal locomotion, feeding, and vertebrate evolution. In my work, I integrate studies across multiple scales from micro-scale structural materials of bone to macro-scale whole bone morphology to evolutionary changes across vertebrate taxa and with comparisons to extinct organisms.

## Current Projects

- Evolution of the avian head: integrating cranial biomechanics, muscle modeling, and brain evolution to understand avian cranial kinesis
- Development of Bayesian and machine learning models for the prediction of craniofacial growth and form in humans
- Effects of exercise and genetic background on skeletal form, physiology, and biomechanics using high activity mice as a model organism

# Awards

```{r awards, results="asis"}
tribble(
  ~ Year, ~ Award,
  2017, "MU School of Medicine Award for Outstanding Preclinical Faculty Education",
  2017, "Ann K. Covington Award for Undergraduate Mentoring",
  2019, "Gold Chalk Award for Graduate Teaching"
) %>%
  detailed_entries(Award, Year)
```

# Grants in Review

\LTXtable{\textwidth}{grants_in_review.tex}

# Current and Past Grants and Fellowships

\LTXtable{\textwidth}{grants.tex}

```{r include=FALSE}
## FIXME Publications

# Gieg AAOSM

# SICB 2021
# McGechie

# AAPA 2021
# Cho
# McGechie

# AAA 2021
# Sellers
# Holliday
# McGechie
# Fortner
# Smolinsky
```

## Dissertation

```{r dissertation}
bib_entries <- bibliography_entries("Paperpile.bib")

if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Dissertation"))
}
```

## Refereed Research Papers

```{r research-papers, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Papers")) %>%
    arrange(issued, author)
}
```

## Manuscripts in Review

```{r in-review, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/In review")) %>%
    arrange(issued, author)
}
```

## Book Chapters

```{r book-chapters, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Book chapters")) %>%
    arrange(issued, author)
}
```

## Invited Reviews

```{r invited-reviews, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Reviews")) %>%
    arrange(issued, author)
}
```

## Book Reviews

```{r book-reviews, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Book reviews")) %>%
    arrange(issued, author)
}
```

## Published Data Sets

```{r datasets, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/Datasets")) %>%
    arrange(issued, author)
}
```

## Manuscripts in Preparation

```{r in-prep, eval=TRUE}
if (include_refs) {
  bib_entries %>%
    filter(str_detect(keyword, "CV/In prep")) %>%
    arrange(author)
}
```
